---
title: "Baby Basic Eye Gaze (study2children)"
author: "Adam Stone, PhD" 
date: '`r format(Sys.Date(), "%m-%d-%Y")`'
output:
  github_document:
    toc: yes
    toc_depth: 2
  html_notebook:
    code_folding: hide
    theme: spacelab
    highlight: tango
    toc: yes
    toc_depth: 2
    toc_float: yes
    df_print: paged
---

# Starting Out

We've cleaned up the data in [03importcleanbabies](03importcleanbabies.nb.html). So we're importing it here. Let's get a chart of how old our babies are.

```{r}
# Libraries
library(tidyverse)
library(feather)
library(scales)
library(stringr)
library(viridis)
library(lme4)
library(lmerTest)
library(RColorBrewer)
#library(cowplot)

# Import data that's been cleaned up from 01importclean
data <- read_feather("cleanedbabyeyedata.feather")

data_ages <- data %>%
  select(participant, language, age, group) %>%
  distinct()

ggplot(data_ages, aes(x = age, fill = language)) + geom_histogram() + facet_grid(language ~ group) + scale_fill_brewer(palette = "Accent")
```

Next, let's do boxplots of each AOI across all stories and kids, grouping for forward vs. reversed. 

```{r}
# Boxplot!
ggplot(data, aes(x = aoi, y = percent, fill = direction)) + 
  geom_boxplot() + theme(axis.text.x = element_text(angle=45, hjust = 1)) +
  ggtitle("Looking Percentages for Each AOI, All Stories") +
  scale_y_continuous(labels = scales::percent, limits = c(0,1))
```

Looks like by far most of the activity is along the Mid** AOIs. Let's look closer. 

```{r}
data_mid <- data %>%
  filter(str_detect(aoi,"Mid") | aoi == "BelowChest")

ggplot(data_mid, aes(x = aoi, y = percent, fill = direction)) + 
  geom_boxplot() + theme(axis.text.x = element_text(angle=45, hjust = 1)) +
  ggtitle("Looking Percentages for Middle AOIs, All Stories") +
  scale_y_continuous(labels = scales::percent, limits = c(0,1))
```

As a preliminary analysis I'm going to just look at MidChestTop and MidFaceBottom. Are there differences based on direction, group, or age for either AOI? 

```{r}
data_mid %>% 
  filter(aoi == "MidChestTop" | aoi == "MidFaceBottom") %>%
  ggplot(aes(x = age, y = percent, color = direction)) + geom_point(alpha = 0.25) +
  geom_smooth(method = "lm") + facet_grid(language ~ aoi) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) +
  ggtitle("Top 2 AOIs")
```

I am not observing big differences for direction. And not strong patterns across age, although there are subtle upward trends for increased chest looking in NSE kids as they get older, but increased face looking in CODAS as they get older.  

What if we defined a Face-Chest Ratio (FCR) such that:

1. MidFaceCenter, MidFaceBottom = Face
1. MidChestTop, MidChestCenter, MidChestBottom, BelowChest = Chest
1. FCR = face - chest / face + chest

Let's try that. Let's also try only MidFaceBottom vs. MidChestTop too, and call that MFCR (for middle of middle).

CHart belows suggests group differences and that CODA babies have a trend to more face-looking while NSE babies don't. 
```{r}
data_mid <- data_mid %>%
  select(-secs, -hits) %>%
  spread(aoi,percent) %>%
  group_by(participant, trial) %>%
  mutate(face = sum(MidFaceCenter, MidFaceBottom, na.rm = TRUE),
         chest = sum(MidChestTop, MidChestCenter, MidChestBottom, BelowChest, na.rm = TRUE),
         fcr = (face - chest) / (face + chest),
         mfcr = (MidFaceBottom - MidChestTop) / (MidFaceBottom + MidChestTop))

ggplot(data_mid, aes(x = age, y = fcr, color = direction)) + geom_point(alpha = 0.25) +
  geom_smooth(method = "lm") + facet_wrap("language") + ggtitle("FaceChest Ratio")
```

Let's also check out MFCR (a stricter ratio). Almost the same thing. 

```{r}
ggplot(data_mid, aes(x = age, y = mfcr, color = direction)) + geom_point(alpha = 0.25) +
  geom_smooth(method = "lm") + facet_wrap("language") + ggtitle("Middle-Middle FaceChest Ratio")
```

So this is rad! Such obvious group differences should also be reflected in a heat map that is collapsed across age and direction. And the heat map below shows that CODAs really focus on the MidFaceBottom AOI, while English-exposed children are a bit more spread out, looking much more at the chest. 

```{r}
data_mid_heat <- data_mid %>%
  ungroup() %>%
  select(-face, -chest, -fcr, -mfcr) %>%
  gather(aoi, percent, BelowChest:MidFaceTop) %>%
  group_by(language, participant, direction, aoi) %>%
  summarise(percent = mean(percent, na.rm = TRUE)) %>%
  group_by(language, direction, aoi) %>%
  summarise(percent = mean(percent, na.rm = TRUE)) %>%
  group_by(language, aoi) %>%
  summarise(percent = mean(percent, na.rm = TRUE)) %>%
  mutate(aoi = factor(aoi, levels = c("BelowChest", "MidChestBottom", "MidChestCenter", "MidChestTop",
                                      "MidFaceBottom", "MidFaceCenter", "MidFaceTop")))

ggplot(data_mid_heat, aes(x = language, y = aoi)) +
  geom_tile(aes(fill=percent),color="lightgray",na.rm=TRUE) + 
  scale_fill_viridis(option = "viridis", direction=-1, limits = c(0,1)) +
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  ylab("") + xlab("") + ggtitle("Eye Gaze Heat Map")
```


# Statistical Testing of FCR/mFCR

Now that we've found something interesting with FCR and mFCR, let's see if it holds up in stats modeling.

## Language, Direction, & Age Predictors

First, a LMM with predictors Language, Direction, and Age, and outcome variable FCR. Nothing significant.

```{r}
fcr_lmm <- lmer(fcr ~ age * language * direction + (1|story) + (1|participant), data = data_mid)
summary(fcr_lmm)
```

Let's repeat the LMM with outcome mFCR. Same thing, although the t values are slightly better.

```{r}
mfcr_lmm <- lmer(mfcr ~ age * language * direction + (1|story) + (1|participant), data = data_mid)
summary(mfcr_lmm)
```

What if we did ANCOVAs (C because age would be a covariate). First, FCR as outcome. 

## Direction & Language Predictors

In the LMMs we've run so far, age is always the worst predictor. So we should have taken that out first, anyway.

Alright, we got an effect of language (p = 0.07) AND an interaction with direction, p = 0.008. CODA babies generally have much higher FCR, but they're also strongly affected by reversal. 

```{r}
fcr_lmm_noage <- lmer(fcr ~ direction * language + (1|story) + (1|participant), data = data_mid)
summary(fcr_lmm_noage)
```

The mFCR LMM gives us similar results. 

```{r}
mfcr_lmm_noage <- lmer(mfcr ~ direction * language + (1|story) + (1|participant), data = data_mid)
summary(mfcr_lmm_noage)
```

## Language as only predictor

**OLD OLD OLD** Same thing here. So it's not age or direction, but language, that has the effect. And that's good! I want to look at forward v. reversed separately next. 
```{r}
fcr_lmm_langonly <- lmer(fcr ~  language + (1|story) + (1|participant) + (1|direction), data = data_mid)
summary(fcr_lmm_langonly)
```

Forward only. Language effect, p = 0.05. 

```{r}
fcr_lmm_langonly_f <- lmer(fcr ~  language + (1|story) + (1|participant), data = filter(data_mid,direction=="forward"))
summary(fcr_lmm_langonly_f)
```

Reversed only. Weaker language effect, p = 0.0131. 

```{r}
fcr_lmm_langonly_r <- lmer(fcr ~  language + (1|story) + (1|participant), data = filter(data_mid,direction=="reversed"))
summary(fcr_lmm_langonly_r)
```

Let's go ahead and plot boxplots to represent LMMs with only language as an important effect. (We can add in direction too). FaceChest Ratio here. 

```{r}
ggplot(data_mid, aes(x = language, y = fcr, fill = language)) + geom_boxplot() + scale_fill_brewer(palette = "Dark2") + ylab("FaceChest Ratio") + ggtitle("FaceChest Ratio by Language")

ggplot(data_mid, aes(x = language, y = fcr, fill = direction)) + geom_boxplot() + ylab("FaceChest Ratio") + ggtitle("FaceChest Ratio by Language & Direction")
```

And Middle-Middle FaceChest Ratio here. 

```{r}
ggplot(data_mid, aes(x = language, y = mfcr, fill = language)) + geom_boxplot() + scale_fill_brewer(palette = "Dark2") + ylab("M-FaceChest Ratio") + ggtitle("Middle-Middle FaceChest Ratio by Language")

ggplot(data_mid, aes(x = language, y = mfcr, fill = direction)) + geom_boxplot() + ylab("M-FaceChest Ratio") + ggtitle("Middle-Middle FaceChest Ratio by Language & Direction")
```




