---
title: "Raw XY Data (study2children)"
author: "Adam Stone, PhD" 
date: '`r format(Sys.Date(), "%m-%d-%Y")`'
output:
  html_notebook:
    code_folding: hide
    theme: spacelab
    highlight: tango
    toc: yes
    toc_depth: 2
    toc_float: yes
    df_print: paged
---

```{r eval=FALSE, include=FALSE}
# This is to get all kids' _processed_ XY data into one single file. Should only run when needed. 
library(tidyverse)
library(feather)

csvpath = "../Child Data/_xydata/"
files <- dir(path = csvpath, pattern = "_xydata")
files <- paste(csvpath, files, sep="")
data <- files %>%
  map(read_csv) %>%
  reduce(rbind) %>%
  mutate(participant = case_when(
    participant == "Ab07ov09_22m" ~ "Ab07ov09_32m",
    TRUE ~ participant
  )) %>%
  mutate(language = case_when(
    participant == "OwenTwin030212_4y2m" ~ "EnglishExposed",
    TRUE ~ language
  ))
write_feather(data, "../Child Data/childxydata.feather")
```

# Participants

Great! At this point, I've run a Matlab script on the children's raw data to collect XY gaze data for each video/trial they viewed. We start with 68 *(now 79 after Dec/Jan batch of 11 kids)* children. Here they are. 

```{r message=FALSE}
# Libraries
library(tidyverse)
library(feather)
library(lme4)
library(grid)
library(png)
library(lmerTest)
#library(cowplot)

# Import data (and fix one participant name, and fix Owen as EnglishExposed)
data <- read_feather("../Child Data/childxydata.feather") %>%
  mutate(x = na_if(x, "NaN"),
         y = na_if(y, "NaN"))

# Get ages
ages <- read_csv("childrenages.csv")
data <- data %>% left_join(ages, by = "participant")
data %>% select(participant,language,age) %>% distinct() %>% arrange(age)  # print data table
```

## Removing Excluded Kids

I excluded all kids that were not included in the AOI analysis. Here is a list of all of 'em!

```{r echo=TRUE}
# Load included babies and children lists
included_babies <- read_feather("cleanedbabyeyedata.feather") %>%
  select(participant) %>% 
  distinct()
included_children <- read_feather("cleanedchildeyedata.feather") %>%
  select(participant) %>%
  distinct()
included <- rbind(included_babies, included_children)

# Use antijoin to see excluded kids
excluded <- anti_join(data, included, by = "participant") %>% 
  select(participant, language, age) %>% 
  distinct()

# Print table
excluded

# Remove excluded kids from main dataset
data <- semi_join(data, included, by = "participant")
```

## Participant Tables and Charts

Let's see a histogram of ages! After this I'll add "baby" and "child" variables so all < 2.0 are identified as babies. 

```{r}
# Histogram of ages
data %>% select(participant,language,age) %>% 
  distinct() %>% 
  ggplot(aes(x = age)) + geom_histogram(fill = "royalblue", binwidth = 0.25) + ggtitle("Ages in Full Dataset")

# Add baby/child agegroup column
data <- data %>% 
  mutate(agegroup = age < 2.0) 
data$agegroup <- as.factor(data$agegroup)
data$agegroup <- fct_recode(data$agegroup, baby = "TRUE", child = "FALSE")
```

And our participant table. 
```{r}
participants_b <- data %>%
  filter(agegroup=="baby") %>%
  select(participant, gender, language, age) %>%
  distinct()

participants_b_n <- participants_b %>%
  count(gender, language) %>%
  spread(gender, n)

participants_b_age <- participants_b %>%
  group_by(language) %>%
  summarise(age_m = round(mean(age), 1), 
            age_sd = round(sd(age), 1),
            age_min = range(age)[1],
            age_max = range(age)[2]) %>%
  mutate(age_range = paste(age_min, age_max, sep = " - ")) %>%
  select(-age_min, -age_max) %>%
  mutate(age_mean = paste(age_m, age_sd, sep = "±")) %>%
  select(-age_m, -age_sd) %>%
  select(language, age_mean, age_range)

participants_table_b <- left_join(participants_b_n, participants_b_age, by = "language") %>%
  add_column(agegroup = "baby")

participants_c <- data %>%
  filter(agegroup=="child") %>%
  select(participant, gender, language, age) %>%
  distinct()

participants_c_n <- participants_c %>%
  count(gender, language) %>%
  spread(gender, n)

participants_c_age <- participants_c %>%
  group_by(language) %>%
  summarise(age_m = round(mean(age), 1), 
            age_sd = round(sd(age), 1),
            age_min = range(age)[1],
            age_max = range(age)[2]) %>%
  mutate(age_range = paste(age_min, age_max, sep = " - ")) %>%
  select(-age_min, -age_max) %>%
  mutate(age_mean = paste(age_m, age_sd, sep = "±")) %>%
  select(-age_m, -age_sd) %>%
  select(language, age_mean, age_range)

participants_table_c <- left_join(participants_c_n, participants_c_age, by = "language") %>%
  add_column(agegroup = "child")

rbind(participants_table_b, participants_table_c) %>% 
  select(language, agegroup, Female, Male, age_mean, age_range)
```

## Save!
Great. Let's save this as `cleanedchildxydata.csv'. 

```{r}
# Pull apart condition columns
data <- data %>%
  separate(condition, into = c("story", "clipnum", "direction", "media"), sep = "_") %>%
  unite(story, clipnum, col = "story", sep = "_") %>%
  select(-media) 

# A bit more cleaning up
data <- data %>%
  mutate(direction = case_when(
    direction == "FW" ~ "forward",
    direction == "ER" ~ "reversed"
  )) %>%
  mutate(language = case_when(
    language == "SignLanguageExposed" ~ "SE",
    language == "EnglishExposed" ~ "NSE"
  )) %>%
  mutate(group = as.factor(group),
         gender = as.factor(gender),
         language = as.factor(language),
         story = as.factor(story),
         direction = as.factor(direction))

# Save as csv and feather (feather preserves column types for R)
write_csv(data,"../Child Data/cleanedchildxydata.csv")
write_feather(data,"../Child Data/cleanedchildxydata.feather")
```

## Any other data cleanup?? 
Do we need to do any other cleanup? I don't think so. 

# Means vs Medians

First, let's trim each participant's data, getting rid of the first 60 samples (0.5 secs). Then we'll get the the mean x and y coordinate for each story for each participant.

```{r}
# Just to load data again 
data <- read_feather("../Child Data/cleanedchildxydata.feather")

data <- data %>%
  group_by(participant,trial) %>%
  slice(60:n())

data_central_tendencies <- data %>%
  group_by(language, agegroup, participant, trial) %>%
  summarise(mean_x = mean(x,na.rm=TRUE),
            mean_y = mean(y,na.rm=TRUE),
            median_x = median(x, na.rm=TRUE),
            median_y = median(y, na.rm=TRUE),
            diff_x = mean_x - median_x,
            diff_y = mean_y - median_y)

means <- data_central_tendencies %>%
  group_by(language, agegroup, participant) %>%
  summarise(mean_x = mean(mean_x, na.rm = TRUE),
            mean_y = mean(mean_y, na.rm = TRUE)) %>%
  group_by(language, agegroup) %>%
  summarise(sd_x = sd(mean_x),
            sd_y = sd(mean_y),
            n = n(),
            mean_x = mean(mean_x),
            mean_y = mean(mean_y)*-1,
            se_x = sd_x/sqrt(n),
            se_y = sd_y/sqrt(n))

means

means_error <- means %>%
  select(-n, -sd_x, -sd_y) %>%
  gather(measure, value, mean_x:se_y) %>%
  separate(measure, into = c("measure","axis")) %>%
  spread(measure, value)

means_error %>%
  filter(axis == "x") %>%
  ggplot(aes(x = agegroup, y = mean, color = language, group = language)) + 
  geom_point(position = position_dodge(width = 0.4)) +
  geom_errorbar(aes(ymin = mean-se, ymax = mean+se), 
                position = position_dodge(width = 0.4), width = 0.25, size = 0.5) + 
  scale_y_continuous(limits = c(0,1080)) +
  coord_flip() + 
  labs(y = "mean along x axis", title = "X-Axis Means")

means_error %>%
  filter(axis == "y") %>%
  ggplot(aes(x = agegroup, y = mean, color = language, group = language)) + 
  geom_point(position = position_dodge(width = 0.4)) +
  geom_errorbar(aes(ymin = mean-se, ymax = mean+se), 
                position = position_dodge(width = 0.4), width = 0.25, size = 0.5) + 
  scale_y_continuous(limits = c(-720,0)) +
  labs(y = "mean along y axis", title = "Y-Axis Means")
```

## Distribution
But is the y-value distribution unimodal, bimodal, normal, what? Do the means represent the only peak? Let's get histograms.

```{r}
ggplot(data, aes(x = y)) + geom_histogram(binwidth = 10) + facet_grid(agegroup ~ language) +
  ggtitle("Histograms of all y-values in all stories")
```

Maybe the mixture of stories and directions throws off the histograms. Let's break it down by "mark" which is an unique number I assigned to each story/direction. Below is a "guide" for each mark. 

```{r fig.height=12}
ggplot(data, aes(x = y)) + geom_histogram(binwidth = 10) + facet_grid(mark ~ agegroup) +
  ggtitle("Histograms of all y-values by each story/mark")

data %>% ungroup() %>% select(mark, story, direction) %>% distinct() %>% arrange(mark)
```

Still seems mostly unimodal (that means one peak, right?). 

## Skewness
But is the data skewed? I've been wondering if we should be using MEDIANS because there can be some extreme x and y values. But Rain said there's been criticism of using medians and that means are better overall. Let's have a look. 

The first chart shows the difference between the mean and the median for each participant and trial. Positive means the mean is bigger than the median, negative means the median is bigger. It shows there is some skew for the y-axis...but the vast majority of differences is less than 50 px so maybe it's okay. 

The second chart shows the means and medians themselves. And the spread is pretty similar between mean and median so maybe using means is fine.

```{r}
data_central_tendencies %>%
  gather(measure, value, diff_x:diff_y) %>%
  ggplot(aes(x = value)) + geom_histogram() + facet_grid(. ~ measure)

data_central_tendencies %>%
  gather(measure, value, mean_x:median_y) %>%
  separate(measure, into = c("measure","axis")) %>%
  ggplot(aes(x = value)) + geom_histogram() + facet_grid(measure ~ axis)
```

## Testing the Means
Let's run a LMM on the means. First, x means for babies. 
```{r}
means <- data %>%
  group_by(language, agegroup, participant, age, story, direction, trial, repetition) %>%
  summarise(x = mean(x, na.rm = TRUE),
            y = mean(y, na.rm = TRUE))

means$repetition = as.factor(means$repetition)
means$trial = as.factor(means$trial)

lmm_baby_mean_x <- lmer(x ~ language * direction + age + 
                          (1|story) + (1|participant) + (1|repetition) + (1|trial), 
                        data = filter(means, agegroup == "baby"))
summary(lmm_baby_mean_x)
```

Y means for babies
```{r}
lmm_baby_mean_y <- lmer(y ~ language * direction + age + 
                          (1|story) + (1|participant) + (1|repetition) + (1|trial), 
                        data = filter(means, agegroup == "baby"))
summary(lmm_baby_mean_y)
```

X means for children
```{r}
lmm_child_mean_x <- lmer(x ~ language * direction + age + 
                          (1|story) + (1|participant) + (1|repetition) + (1|trial), 
                        data = filter(means, agegroup == "child"))
summary(lmm_child_mean_x)
```

Y means for children
```{r}
lmm_child_mean_y <- lmer(y ~ language * direction + age + 
                          (1|story) + (1|participant) + (1|repetition) + (1|trial), 
                        data = filter(means, agegroup == "child"))
summary(lmm_child_mean_y)
```

Let's try it with both kids and babies. 
```{r}
lmm_all_mean_x <- lmer(x ~ language * direction * agegroup + 
                          (1|story) + (1|participant) + (1|repetition) + (1|trial), 
                        data = means)
summary(lmm_all_mean_x)
lmm_all_mean_y <- lmer(y ~ language * direction * agegroup + 
                          (1|story) + (1|participant) + (1|repetition) + (1|trial), 
                        data = means)
summary(lmm_all_mean_y)
```

## Summary
No difference in the mean looking position for x or y in children or babies! But if we put children and babies in the same dataset we get a significant main effect of children vs. babies. Okay. 

# Plotting One Kid

And I can get x or y plots of one participant across 8 stories. Let's do Emmet. We'll set the x and y limits to the whole width of the Tobii monitor (1600x1200...or is it now 1080x720). But because Tobii considers (0,0) to be the upper left corner (and not the bottom left corner), we also need to flip the y axis. 

```{r}
emmet <- filter(data,participant=="emmet_12_10_12_CODA") %>% mutate(y = y*-1)
ggplot(emmet,aes(x=x,y=y,color=story)) + geom_point(size=0.1) + geom_path() + facet_grid(repetition ~ story) + guides(color="none") + scale_x_continuous(limit=c(0,1080)) + scale_y_continuous(limit=c(-720,0))
```

Cool, yeah? 

# Viewing Space (SD)
To measure viewing space, we can use standard deviation or IQR. Generally, if we're using means, we should use standard deviations. If we're using medians, we should use IQR. That's my thinking, anyway. 

We'll try SDs first. Let's try the first SD, which is the middle 68% of the data. 

```{r}
sd <- data %>%
  group_by(participant, trial) %>%
  summarise(mean_x = mean(x, na.rm = TRUE),
            mean_y = mean(y, na.rm = TRUE),
            sd_x = sd(x, na.rm = TRUE),
            sd_y = sd(y, na.rm = TRUE)) %>%
  ungroup()
head(sd,10)

# join participant info back
participantinfo <- data %>%
  select(participant, trial, age, group, agegroup, gender, language, story, direction, mark, repetition) %>%
  distinct()
sd <- left_join(sd, participantinfo, by = c("participant","trial"))
```

And check out the histograms. I truncated the y-axis at 50 counts to better see outliers. 

```{r}
sd %>% 
  gather(axis,sd,sd_x:sd_y) %>%
  ggplot(aes(x=sd,fill=axis)) + geom_histogram() + facet_grid(axis~.) + 
  coord_cartesian(ylim = c(0,50))
```

So there are some really high outliers where the SD is 150 or 200 pixels in one direction (so a spread of as high as 400 pixels, which is a lot! I want to see those cases to see if they should be taken out or if we don't need to worry about them. 

> It may be useful to think about getting rid of outliers. We should keep this in mind...

```{r}

xoutliers <- sd %>%
  arrange(desc(sd_x)) %>%
  slice(1:20)
youtliers <- sd %>%
  arrange(desc(sd_y)) %>%
  slice(1:20)
xoutliers
youtliers

```

## Testing
First, does reversal and language experience have an effect on the SD? Babies, x-axis first. 

```{r}
sd$trial <- as.factor(sd$trial)
sd$repetition <- as.factor(sd$repetition)

sd_x_baby <- lmer(sd_x ~ direction * language + age + (1|participant) + (1|story) + (1|repetition) + (1|trial), data = filter(sd, agegroup == "baby"))
summary(sd_x_baby)
```

That's fine, we're not exactly predicting changes along the x-axis. The y-axis is what we are really interested in! :) 
```{r}
sd_y_baby <- lmer(sd_y ~ direction * language + age + (1|participant) + (1|story) + (1|repetition) + (1|trial), data = filter(sd, agegroup == "baby"))
summary(sd_y_baby)
```

Now children, x-axis
```{r}
sd_x_child <- lmer(sd_x ~ direction * language + age + (1|participant) + (1|story) + (1|repetition) + (1|trial), data = filter(sd, agegroup == "child"))
summary(sd_x_child)
```

And children, y-axis
```{r}
sd_y_child <- lmer(sd_y ~ direction * language + age + (1|participant) + (1|story) + (1|repetition) + (1|trial), data = filter(sd, agegroup == "child"))
summary(sd_y_child)
```

And now all babies/children, x axis
```{r}
sd_x_all <- lmer(sd_x ~ direction * language * agegroup + (1|participant) + (1|story) + (1|repetition) + (1|trial), data = sd)
summary(sd_x_all)
```

```{r}
sd_y_all <- lmer(sd_y*2 ~ direction * language * agegroup + (1|participant) + (1|story) + (1|repetition) + (1|trial), data = sd)
summary(sd_y_all)
```

## Summary
So there is no effect of language or direction (or interactions) on the standard deviation. Among babies, there seems to be an effect of age on y-axis viewing space such that it narrows the older the baby is (p = 0.046). 

When we put babies and children together, we see age group differences for sd_x and sd_y, not surprisingly. 


# Everything after this needs to be updated.

# Viewing Space (IQR)

Now let's get the middle 50% (aka the IQR) of x and y for each participant's story (we've already trimmed the first 60 samples). That should also take care of further weird outliers. And we are defining "viewing space" as the IQR of the x and y axis. 

```{r}
iqr <- data %>%
  group_by(participant,trial) %>%
  summarise(xIQR = IQR(x,na.rm=TRUE),
                   yIQR = IQR(y,na.rm=TRUE),
                   xmed = median(x, na.rm=TRUE),
                   ymed = median(y, na.rm=TRUE)) %>%
  ungroup()
head(iqr,10)

# Join participant info back into IQR table
participantinfo <- data %>%
  select(participant, trial, age, group, gender, language, story, direction, mark, repetition) %>%
  distinct()

iqr <- left_join(iqr, participantinfo, by = c("participant","trial"))
```

And check out the histograms. I truncated the y-axis at 100 to better see outliers. 

```{r}
iqr %>% 
  gather(axis,iqr,xIQR:yIQR) %>%
  ggplot(aes(x=iqr,fill=axis)) + geom_histogram() + facet_grid(axis~.) + 
  coord_cartesian(ylim = c(0,50))
```

So we see some outliers. Who are those? Let's get a table of them. Review those AFTER I've done the cleanups of course. 

```{r}
xoutliers <- iqr %>%
  arrange(desc(xIQR)) %>%
  slice(1:10)
youtliers <- iqr %>%
  arrange(desc(yIQR)) %>%
  slice(1:10)
```

Next, check the medians.

```{r}
iqr %>% 
  gather(axis,med,xmed:ymed) %>%
  ggplot(aes(x=med,fill=axis)) + geom_histogram() + facet_grid(axis~.) + 
  coord_cartesian(ylim = c(0,50))
```

SO I need to review those too. After cleaning up/removing kids.

```{r}
iqr.gather <- iqr %>% gather(axis,value,xIQR:ymed)
iqr.iqr <- filter(iqr.gather,axis=="xIQR" | axis=="yIQR")
iqr.med <- filter(iqr.gather,axis=="xmed" | axis=="ymed")


ggplot(iqr.iqr,aes(x=language,y=value,fill=direction)) + 
  geom_boxplot() + theme(axis.text.x=element_text(angle=45,hjust=1)) +
  facet_grid(.~axis)
```

And the median x and y position (this assumes all calibrations are correct):

```{r}
ggplot(iqr.med,aes(x=language,y=value,fill=direction)) + 
  geom_boxplot() + theme(axis.text.x=element_text(angle=45,hjust=1)) +
  facet_grid(.~axis)
```

First, does reversal and language experience have an effect on X IQR? We have random intercepts for each participant and media, and a random slope adjustment for reversed for each participant. 

```{r}
xiqr.reversal <- lmer(xIQR ~ direction * language + (direction|participant) + (1|story), data = iqr)
summary(xiqr.reversal)$coefficients
```

That's fine, we're not exactly predicting changes along the x-axis. The y-axis is what we are really interested in! :) 
```{r}
yiqr.reversal <- lmer(yIQR ~ direction * language + (direction|participant) + (1|story), data = iqr)
summary(yiqr.reversal)$coefficients
```


# Viewing Space Charts
I want to learn how to make rectangle plots so here we go. Using each participant's four x and y medians and 4 x and y IQRs (one set for each story, for 4 stories). So I can get the logic and code down. Let's assume all calibrations were correct. Here's the chart for the whole media size of 1440x1080 (as reported in Tobii). 
```{r}
# In this order, we'll get a grand median by taking a participant's median across their 4 stories, than the median for forward and reverse across all participants. 
medians <- iqr %>%
  group_by(participant,direction) %>%
  summarise(xIQR = median(xIQR,na.rm=TRUE),
                   yIQR = median(yIQR,na.rm=TRUE),
                   xmed = median(xmed,na.rm=TRUE),
                   ymed = median(ymed,na.rm=TRUE)) %>%
  group_by(direction) %>% 
  summarise(xIQR = median(xIQR,na.rm=TRUE),
                   yIQR = median(yIQR,na.rm=TRUE),
                   x = median(xmed,na.rm=TRUE),
                   y = median(ymed,na.rm=TRUE))

medians <- medians %>%
  mutate(y = y*-1,
         xmin = x-(xIQR/2),
         xmax = x+(xIQR/2),
         ymin = y-(yIQR/2),
         ymax = y+(yIQR/2))

img <- readPNG("cindy.png")
g <- rasterGrob(img, interpolate=TRUE, width=unit(1,"npc"), height=unit(1,"npc")) 

ggplot(medians, aes(fill=direction,color=direction)) +
  annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
  geom_rect(aes(xmin=xmin,ymin=ymin,xmax=xmax,ymax=ymax),alpha=.1) + 
  theme_minimal() + xlim(0,1440) + ylim(-1080,0)


# ggplot(iqr.global, aes(fill=direction,color=direction)) +
#   annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
#   geom_rect(aes(xmin=xmin,ymin=ymin,xmax=xmax,ymax=ymax),alpha=.1) + 
#   theme_minimal() + xlim(0,1440) + ylim(-1080,0) +
#   geom_hline(yintercept=-1080+885) +
#   geom_hline(yintercept=-1080+525) + 
#   annotate(geom="text", x = 300, y = -1080+555, label = "upper shoulder point") +
#   annotate(geom="point", x = 535, y = -1080+525) + 
#   annotate(geom="text", x = 535, y = -1080+910, label = "height line") + 
#   annotate(geom="rect", xmin = 535, xmax = 535+365, ymin = -525-551, ymax = -1080+525, fill="maroon", color="black", alpha=0.5) + 
#   annotate(geom="text", x = 700, y = -900, label = "torso")

```

# Viewing Space Charts for Individuals
Now let's see the variation in viewing spaces for all our individuals. Should be fun.

```{r fig.height=10, fig.width=26}
iqr.individuals <- iqr %>%
  rename(x = xmed,
         y = ymed) %>%
  mutate(y = y*-1,
         xmin = x-(xIQR/2),
         xmax = x+(xIQR/2),
         ymin = y-(yIQR/2),
         ymax = y+(yIQR/2))

ggplot(iqr.individuals, aes(fill=direction,color=direction)) +
  annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
  geom_rect(aes(xmin=xmin,ymin=ymin,xmax=xmax,ymax=ymax),alpha=.1) + 
  theme_minimal() + xlim(0,1440) + ylim(-1080,0) + facet_wrap("direction") +
  ggtitle("with IQRs")
```

Now let's make Outer Limits charts which is IQR +/- 2 SDs.  But I want to change that because I don't like the idea of mixing IQRs and SDs. 
```{r fig.height=10, fig.width=26}
# sd.individuals <- select(sd.individuals,participant,media,xsd,ysd)
# iqrsd.individuals <- left_join(iqr.individuals,sd.individuals,by=c("participant","media")) %>%
#   mutate(xmin = xmin-(2*xsd),
#          xmax = xmax+(2*xsd),
#          ymin = ymin-(2*ysd),
#          ymax = ymax+(2*ysd))
# 
# ggplot(iqrsd.individuals, aes(fill=direction,color=direction)) +
#   annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
#   geom_rect(aes(xmin=xmin,ymin=ymin,xmax=xmax,ymax=ymax),alpha=.1) + 
#   theme_minimal() + xlim(0,1440) + ylim(-1080,0) + facet_wrap("direction") +
#   ggtitle("with SDs")
```

```{r fig.height=10, fig.width=26}
# iqrsd.individuals <- iqrsd.individuals %>%
#   group_by(direction) %>%
#   dplyr::summarize(x = mean(x,na.rm=TRUE),
#             y = mean(y,na.rm=TRUE),
#             xmin = mean(xmin,na.rm=TRUE),
#             ymin = mean(ymin,na.rm=TRUE),
#             xmax = mean(xmax,na.rm=TRUE),
#             ymax = mean(ymax,na.rm=TRUE))
# ggplot(iqrsd.individuals, aes(fill=direction,color=direction)) +
#   annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
#   geom_rect(aes(xmin=xmin,ymin=ymin,xmax=xmax,ymax=ymax),alpha=.1) + 
#   theme_minimal() + xlim(0,1440) + ylim(-1080,0) + facet_wrap("direction") +
#   ggtitle("Average of above chart (rain's outer limits)")

```

# Within-Subject Variation

Just read [this good post](https://mvuorre.github.io/post/2017/within-subject-scatter/) about plotting within-subject variation and saw it can really apply to this dataset. So I'm going to try out one example. 

We know the y means aren't significantly different across groups but that's been hard to visualize on a per-subject basis (or even from an error bar chart since the error bars are so small). Let's visualize that!

```{r}
# First get the mean of each trial, THEN the participant-level means
within_subjects <- data %>%
  group_by(participant, agegroup, language, direction, trial) %>%
  summarise(y = mean(y, na.rm = TRUE),
            count = n()) %>%
  group_by(participant, agegroup, language, direction) %>%
  summarise(mean = mean(y, na.rm = TRUE),
            se = sd(y, na.rm = TRUE)/sqrt(n()),
            count = n())

# Then spread out mean and SE columns by direction
within_subjects_means <- within_subjects %>%
  select(-se, -count) %>%
  spread(direction, mean, sep = "_")

within_subjects_se <- within_subjects %>%
  select(-mean, -count) %>%
  spread(direction, se, sep = "SE")

within_subjects <- left_join(within_subjects_means, within_subjects_se)

# Now let's plot just the means
lims <- c(min(data$y, na.rm = T)+100, max(data$y, na.rm = T)-200)
within_subjects %>%
  ggplot(aes(x = direction_forward, y = direction_reversed, color = language)) +
  geom_point() + 
  geom_abline() +
  theme(aspect.ratio = 1) + 
  scale_x_continuous("forward", limits = lims) +
  scale_y_continuous("reversed", limits = lims) +
  ggtitle("Y Axis Means") +
  facet_wrap("agegroup")

# now with error bars
within_subjects %>%
  ggplot(aes(x = direction_forward, y = direction_reversed, color = language)) +
  geom_point(size = 2) + 
  geom_errorbar(aes(ymin=direction_reversed-directionSEreversed, ymax=direction_reversed+directionSEreversed)) +
  geom_errorbarh(aes(xmin=direction_forward-directionSEforward, xmax=direction_forward+directionSEforward)) +
  geom_abline() +
  theme(aspect.ratio = 1) + 
  scale_x_continuous("forward", limits = c(140,460)) +
  scale_y_continuous("reversed", limits = c(140,460)) +
  ggtitle("Y Axis Means") +
  facet_wrap("agegroup")
```

