---
title: "Babies - Three Experiments"
author: "Adam Stone, PhD" 
date: '`r format(Sys.Date(), "%m-%d-%Y")`'
output:
  html_notebook:
    code_folding: hide
    theme: spacelab
    highlight: tango
    toc: yes
    toc_depth: 2
    toc_float: yes
    df_print: paged
---

This is hopefully the results section for three baby experiments we have done: 

1. NSE babies, signs v. gestures
2. NSE babies, ASL stories
3. SE babies, ASL stories

Across all studies, we are using baby age groups as such:

* Younger babies = 5 to 8.99 months
* Older babies = 9.0 to 13.99 months

# 1. NSE Babies Signs & Gestures

Who are our babies in Experiment 1? 
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(janitor)
library(lme4)
library(scales)

exp1data <- read_csv("study1cleaneddata.csv") %>%
  filter(signer == "Non-signer") %>%
  select(name, age, gender, media, video, type, direction, sec, aoi, percent) %>%
  filter(age <= 18) %>%
  mutate(agegroup = case_when(
    age <= 8.99 ~ "younger",
    age >= 9.0 ~ "older"
  )) %>%
  filter(!is.na(agegroup))

exp1data$agegroup <- fct_relevel(exp1data$agegroup, c("younger","older"))

exp1data %>%
  select(name, age, agegroup, gender) %>%
  distinct() %>%
  group_by(agegroup) %>%
  summarise(N = n(),
            age = mean(age)) %>%
  print()

exp1data %>%
  select(name, age, agegroup, gender) %>%
  distinct() %>%
  group_by(agegroup, gender) %>%
  summarise(N = n()) %>%
  spread(gender, N) %>%
  print()
```

Okay, so this experiment has three main factors: 

1. Age (Older v. Younger) 
2. Type (Sign v. Gesture) 
3. Direction (Forward v. Reversed)

What did overall looking behavior look like, regardless of direction? 

```{r}
# I calculated percent wrong; get total secs per media for denominator
exp1data <- exp1data %>%
  group_by(agegroup, name, type, direction, media) %>%
  mutate(total_sec = sum(sec),
         percent = sec/total_sec)

exp1data_overall_looking <- exp1data %>%
  filter(aoi %in% c("belly","belowchest","midchestbottom","midchestcenter","midchesttop","midfacebottom",
                    "midfacecenter","midfacetop")) %>%
  group_by(agegroup, type, name, direction, media) %>%
  summarise(percent = sum(percent)) %>% # gets total looking time (secs) for each video for each baby
  group_by(agegroup, type, direction, name) %>%
  summarise(percent = mean(percent)) # gets average looking time (secs) for each baby

exp1data_overall_looking %>% 
  group_by(agegroup, direction, type) %>%
  summarise(mean_percent = mean(percent),
            count = n(),
            sd = sd(percent),
            se = sd/sqrt(count)) %>%
  ggplot(aes(x = direction, y = mean_percent, fill = type)) + 
  geom_col(position = "dodge") + 
  geom_errorbar(aes(ymin = mean_percent - se, ymax = mean_percent + se), position = "dodge") + 
  scale_y_continuous(limits = c(0,1)) +
  facet_wrap("agegroup") + theme_minimal()
```

# 2. NSE ASL Stories

Who are our babies in Experiment 2? 

```{r message=FALSE, warning=FALSE}
library(feather)

exp2data <- read_feather("cleanedbabyeyedata.feather") %>%
  filter(language == "english") %>%
  mutate(age = age*12) %>%
  select(participant, age, gender, story, direction, mark, trial, repetition, aoi, secs, percent) %>%
  rename(name = participant) %>%
  mutate(agegroup = case_when(
    age <= 8.99 ~ "younger",
    age >= 9.0 ~ "older"
  )) %>%
  filter(!is.na(agegroup))

exp2data$agegroup <- fct_relevel(exp2data$agegroup, c("younger","older"))

exp2data %>%
  select(name, age, agegroup, gender) %>%
  distinct() %>%
  group_by(agegroup) %>%
  summarise(N = n(),
            age = mean(age)) %>%
  print()

exp2data %>%
  select(name, age, agegroup, gender) %>%
  distinct() %>%
  group_by(agegroup, gender) %>%
  summarise(N = n()) %>%
  spread(gender, N) %>%
  print()
```

Experiment 2 has two main factors: 

1. Age (Older v. Younger) 
2. Direction (Forward v. Reversed)

```{r}
exp2data_overall_looking <- exp2data %>%
  group_by(agegroup, direction, name, story, repetition) %>%
  summarise(percent = sum(percent)) %>% # gets total looking time (secs) for each video for each baby
  group_by(agegroup, direction, name) %>%
  summarise(percent = mean(percent)) # gets average looking time (secs) for each baby

exp2data_overall_looking %>% 
  group_by(agegroup, direction) %>%
  summarise(mean_percent = mean(percent),
            count = n(),
            sd = sd(percent),
            se = sd/sqrt(count)) %>%
  ggplot(aes(x = agegroup, y = mean_percent, fill = direction)) + 
  geom_col(position = "dodge") + 
  geom_errorbar(aes(ymin = mean_percent - se, ymax = mean_percent + se), position = "dodge") + 
  scale_y_continuous(limits = c(0,1)) +
  theme_minimal()
```

# 3. SE ASL Stories

Who are our babies in Experiment 3? 

```{r message=FALSE, warning=FALSE}
library(feather)

exp3data <- read_feather("cleanedbabyeyedata.feather") %>%
  filter(language == "sign") %>%
  mutate(age = age*12) %>%
  select(participant, age, gender, story, direction, mark, trial, repetition, aoi, secs, percent) %>%
  rename(name = participant) %>%
  mutate(agegroup = case_when(
    age <= 8.99 ~ "younger",
    age >= 9.0 ~ "older"
  )) %>%
  filter(!is.na(agegroup))

exp3data$agegroup <- fct_relevel(exp3data$agegroup, c("younger","older"))

exp3data %>%
  select(name, age, agegroup, gender) %>%
  distinct() %>%
  group_by(agegroup) %>%
  summarise(N = n(),
            age = mean(age)) %>%
  print()

exp3data %>%
  select(name, age, agegroup, gender) %>%
  distinct() %>%
  group_by(agegroup, gender) %>%
  summarise(N = n()) %>%
  spread(gender, N) %>%
  print()
```

Experiment 3 has two main factors: 

1. Age (Older v. Younger) 
2. Direction (Forward v. Reversed)

```{r}
exp3data_overall_looking <- exp3data %>%
  group_by(agegroup, direction, name, story, repetition) %>%
  summarise(percent = sum(percent)) %>% # gets total looking time (secs) for each video for each baby
  group_by(agegroup, direction, name) %>%
  summarise(percent = mean(percent)) # gets average looking time (secs) for each baby

exp3data_overall_looking %>% 
  group_by(agegroup, direction) %>%
  summarise(mean_percent = mean(percent),
            count = n(),
            sd = sd(percent),
            se = sd/sqrt(count)) %>%
  ggplot(aes(x = agegroup, y = mean_percent, fill = direction)) + 
  geom_col(position = "dodge") + 
  geom_errorbar(aes(ymin = mean_percent - se, ymax = mean_percent + se), position = "dodge") + 
  scale_y_continuous(limits = c(0,1)) +
  theme_minimal()
```