---
title: "Babies - Study 2 - Results"
output: 
  html_notebook:
    code_folding: hide
    theme: spacelab
    highlight: tango
    toc: yes
    toc_depth: 2
    toc_float: yes
    df_print: paged
---

This is hopefully the results section for the Study 2 NSE & SE babies watching ASL Stories. We have two main factors: 

1. Language (Sign v. English)
1. Direction (Forward v. Reversed)

Ages of babies are from 5 to 14.99 months. That means we lose two "old" CODA babies - Janine (16 mo) and za02 (23 mo). The dataset also contains factors for younger v. older babies *IF* we want to do age group splits. I do not recommend it because we lose all significance that way and we have more precise age information, better than brute groups.  IF we do use it, the baby age groups are such:

* Younger babies = 5 to 8.99 months
* Older babies = 9.0 to 14.99 months

To skip to the XY Data, go here. 
To skip to the AOI/FCR analysis, go here. 

# Demographics
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(janitor)
library(lme4)
library(lmerTest)
library(scales)
library(feather)
library(GGally)

# Grab data that was produced in 03importcleanbabies.Rmd
babies <- read_feather("cleanedbabyeyedata.feather") %>%
  mutate(age = age*12) %>%
  select(participant, language, age, gender, story, direction, mark, trial, repetition, aoi, secs, percent) %>%
  rename(name = participant) %>%
  mutate(agegroup = case_when(
    age <= 8.99 ~ "younger",
    age >= 9.0 & age < 15 ~ "older"
  )) %>%
  filter(!is.na(agegroup)) %>%
  mutate(language = case_when(
    language == "english" ~ "NSE",
    language =="sign" ~ "SE"
  )) %>%
  rename(lang = language)

babiesinfo <- babies %>%
  select(name, lang, age, gender) %>%
  distinct() %>%
  group_by(lang) %>%
  summarise(N = n(),
            age_mean = mean(age),
            sd = sd(age),
            min = min(age),
            max = max(age))

genders <- babies %>%
  select(name, lang, age, gender) %>%
  distinct() %>%
  group_by(lang, gender) %>%
  summarise(N = n()) %>%
  spread(gender, N)

babiesinfo <- left_join(babiesinfo, genders) %>%
  select(lang, N, Female, Male, age_mean, sd, min, max) %>%
  print()

babies$agegroup <- fct_relevel(babies$agegroup, c("younger","older"))


# IF we do age groups, use this code
# 
# babiesinfo <- babies %>%
#   select(name, lang, age, agegroup, gender) %>%
#   distinct() %>%
#   group_by(lang, agegroup) %>%
#   summarise(N = n(),
#             age_mean = mean(age),
#             sd = sd(age),
#             min = min(age),
#             max = max(age))
# 
# genders <- babies %>%
#   select(name, lang, age, agegroup, gender) %>%
#   distinct() %>%
#   group_by(lang, agegroup, gender) %>%
#   summarise(N = n()) %>%
#   spread(gender, N)
# 
# babiesinfo <- left_join(babiesinfo, genders) %>%
#   select(lang, agegroup, N, Female, Male, age_mean, sd, min, max) %>%
#   print()

```

# Global Looking

We calculated percentages *based on overall clip length* as the denominator. In this way, we can meaningfully contrast looking times at the videos (which are variable lengths) based on different factors. But when we go to AOI analysis we need to re-calculate the percentages so the denominator is based on total looking time, not overall clip length. 

The chart below shows little differences based on factors Age, Language, or Direction. That's good, means the videos were equally engaging for all babies, right? 

```{r}
babies$lang <- as.factor(babies$lang)
babies_overall_looking <- babies %>%
  group_by(name, age, lang, direction, story, repetition) %>%
  summarise(percent = sum(percent)) # gets total looking percent for each trial for each baby

# Table of means
babies_overall_looking %>% 
  group_by(name, lang, direction) %>%
  summarise(percent = mean(percent)) %>% # get average looking percent for each baby
  group_by(lang, direction) %>%
  summarise(mean_percent = mean(percent),
            count = n(),
            sd = sd(percent),
            se = sd/sqrt(count)) %>%
  select(-sd) %>%
  print()

ggplot(babies_overall_looking, aes(x = age, y = percent, color = direction, fill = direction)) + 
  geom_jitter(alpha = 0.5) +
  facet_grid(. ~ lang) +
  geom_smooth(method = "lm", se = FALSE) +
  ggtitle("Video Attention") +
  xlab("age (months)") +
  ylab("percent looking") + 
  theme_bw() + 
  scale_y_continuous(limits = c(0,1), labels = percent) 


# Plot
# babies_overall_looking %>% 
#   group_by(lang, direction, name) %>%
#   summarise(percent = mean(percent)) %>% # gets average looking percent for each baby
#   group_by(lang, direction) %>%
#   summarise(mean_percent = mean(percent), # gets group averages
#             count = n(),
#             sd = sd(percent),
#             se = sd/sqrt(count)) %>% 
#   ggplot(aes(x = lang, y = mean_percent, fill = direction)) + 
#   geom_col(position = "dodge") + 
#   geom_errorbar(aes(ymin = mean_percent - se, ymax = mean_percent + se), 
#                 position = position_dodge(width = 0.9), width = 0.25) + 
#   scale_y_continuous(limits = c(0,1), labels = percent) +
#   theme_minimal() + 
#   theme(panel.grid.major.x = element_blank()) +
# #  facet_wrap("lang") +
#   ggtitle("Video Attention") +
#   xlab("") +
#   ylab("percent looking")

# babies_overall_looking %>%
#   ggplot(aes(x = lang, y = percent, fill = direction)) +
#   facet_wrap("agegroup") + 
#   geom_violin()
```

A linear model shows there were no significant effects of any factors. We can conclude there was no effect on how *much* the babies looked at the stimuli.  

```{r}
global_lm <- lmer(percent ~ age + lang * direction + (direction|name) + (direction|story), data = babies_overall_looking)
summary(global_lm) 
ggcoef(global_lm)
```

# AOI Looking
Now we'll re-calculate the percentages so the denominator is based on total looking time. All AOIs should sum up to 100% for each trial and each baby. Next let's make a boxplot of all AOIs. 

```{r}
#Recalculate percent
babies <- babies %>%
  select(-percent) %>%
  group_by(name, lang, agegroup, age, direction, story, mark, trial, repetition) %>%
  mutate(totalsec = sum(secs)) %>%
  group_by(name, lang, agegroup, age, direction, story, mark, trial, repetition, aoi) %>%
  summarise(percent = secs/totalsec)

# Boxplot
babies %>%
  ggplot(aes(x = aoi, y = percent, fill = direction)) + 
  geom_boxplot() +
  ggtitle("AOI Attention") +
  theme_bw() + 
  xlab("") +
  theme(axis.text.x = element_text(angle=45, hjust = 1),
        panel.grid.major.x = element_blank()) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1))
```
It appears two important AOIs are MidChestTop and MidFaceBottom. Let's look again only at midline AOIs:

```{r}
midline = c("Belly","BelowChest","MidChestBottom","MidChestCenter","MidChestTop",
            "MidFaceBottom","MidFaceCenter","MidFaceTop")
babies %>%
  filter(aoi %in% midline) %>%
  ggplot(aes(x = aoi, y = percent, fill = direction)) + 
  geom_boxplot() +
  ggtitle("Midline AOI Attention") +
  theme_bw() + 
  xlab("") +
  theme(axis.text.x = element_text(angle=45, hjust = 1),
        panel.grid.major.x = element_blank()) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1))
```

I'm going to run linear models with only MidChestTop or MidFaceBottom, and see what happens. No age interactions.

**MidChestTop:**

* Significant effect of age (p = 0.019) - older babies look at MidChestTop AOI more.
* Significant effect of language (p = 0.040) - NSE babies look +12.3% more than SE babies. 
* Significant effect of direction (p = 0.047) - Babies look about 4.5% less for reversed
* No language X direction interaction. 

**MidFaceBottom:** 

* No effect of age
* Significant effect of language (p = 0.038) - SE babies look +16% more than NSE babies.
* Marginal effect of language (p = 0.069) - Babies look about 4% more for reversed. 
* No language X direction interaction.


```{r}
babies %>%
  filter(aoi %in% c("MidFaceBottom","MidChestTop")) %>%
  ggplot(aes(x = age, y = percent, color = direction, fill = direction)) + 
  geom_jitter(alpha = 0.5) + 
  geom_smooth(method = "lm", se = FALSE) +
  scale_y_continuous(limits = c(0,1), labels = percent) +
  theme_bw() + 
#  theme(panel.grid.major.x = element_blank()) +
  facet_grid(aoi ~ lang) +
  ggtitle("AOI Attention") +
  xlab("") +
  ylab("percent looking")

midchesttop_lm <- lmer(percent ~ age + lang * direction + (1|name) + (1|story), data = filter(babies, aoi == "MidChestTop"))
summary(midchesttop_lm)
ggcoef(midchesttop_lm)

midfacebottom_lm <- lmer(percent ~ age + lang * direction + (1|name) + (1|story), data = filter(babies, aoi == "MidFaceBottom"))
summary(midfacebottom_lm)
ggcoef(midfacebottom_lm)

# Bar chart
# babies %>%
#   filter(aoi %in% c("MidFaceBottom","MidChestTop")) %>%
#   group_by(agegroup, lang, direction, name, aoi) %>%
#   summarise(percent = mean(percent)) %>% # gets average looking percent for each baby
#   group_by(agegroup, lang, direction, aoi) %>%
#   summarise(mean_percent = mean(percent), # gets group averages
#             count = n(),
#             sd = sd(percent),
#             se = sd/sqrt(count)) %>% 
#   ggplot(aes(x = lang, y = mean_percent, fill = direction)) + 
#   geom_col(position = "dodge") + 
#   geom_errorbar(aes(ymin = mean_percent - se, ymax = mean_percent + se), 
#                 position = position_dodge(width = 0.9), width = 0.25) + 
#   scale_y_continuous(limits = c(0,1), labels = percent) +
#   theme_minimal() + 
#   theme(panel.grid.major.x = element_blank()) +
#   facet_grid(aoi ~ agegroup) +
#   ggtitle("Video Attention") +
#   xlab("") +
#   ylab("percent looking")
```


# Face-Chest Ratio
Next, we'll define a Face-Chest Ratio (FCR) such that:

1. MidFaceCenter, MidFaceBottom = Face
1. MidChestTop, MidChestCenter, MidChestBottom, BelowChest = Chest
1. FCR = face - chest / face + chest

We did not include Belly or MidFaceTop because of very low looking rates according to the boxplots above.

```{r}
babies_fcr <- babies %>%
  spread(aoi,percent) %>%
  group_by(name, age, agegroup, lang, direction, story, repetition) %>%
  summarise(face = sum(MidFaceCenter, MidFaceBottom, na.rm = TRUE),
         chest = sum(MidChestTop, MidChestCenter, MidChestBottom, BelowChest, na.rm = TRUE),
         fcr = (face - chest) / (face + chest))

# Table of means
babies_fcr %>% 
  group_by(lang, direction, name) %>%
  summarise(fcr = mean(fcr)) %>% # gets average looking percent for each baby
  group_by(lang, direction) %>%
  summarise(mean_fcr = mean(fcr), # gets group averages
            count = n(),
            sd = sd(fcr),
            se = sd/sqrt(count)) %>%
  select(-sd) %>%
  print()

# Plot
ggplot(babies_fcr, aes(x = age, y = fcr, color = direction, fill = direction)) + 
  geom_jitter(alpha = 0.5) + 
  geom_smooth(method = "lm", se = FALSE) +
  scale_y_continuous(limits = c(-1,1)) +
  theme_bw() + 
  theme(panel.grid.major.x = element_blank()) +
  facet_grid(. ~ lang) +
  ggtitle("Face-Chest Ratios") +
  xlab("") +
  ylab("FCR")

# Bar chart
# babies_fcr %>% 
#   group_by(agegroup, lang, direction, name) %>%
#   summarise(fcr = mean(fcr)) %>% # gets average looking percent for each baby
#   group_by(agegroup, lang, direction) %>%
#   summarise(mean_fcr = mean(fcr), # gets group averages
#             count = n(),
#             sd = sd(fcr),
#             se = sd/sqrt(count)) %>% 
#   ggplot(aes(x = lang, y = mean_fcr, fill = direction)) + 
#   geom_col(position = "dodge") + 
#   geom_errorbar(aes(ymin = mean_fcr - se, ymax = mean_fcr + se), 
#                 position = position_dodge(width = 0.9), width = 0.25) + 
#   scale_y_continuous(limits = c(-1,1)) +
#   theme_minimal() + 
#   theme(panel.grid.major.x = element_blank()) +
#   facet_wrap("agegroup") +
#   ggtitle("Face-Chest Ratios") +
#   xlab("") +
#   ylab("FCR")
```

What will a linear mixed model tell us? (with no age interactions)

* No effect of age. Interesting. Maybe just becuase we don't have that many babies. 
* Weak effect of language: SE babies have overall +0.38 FCR than NSE babies (p = 0.063); in other words athey are more attracted to the face. But only marginally. **Before Victoria it was p = 0.018, with +0.49 FCR for SE.**
* Effect of direction: Reversal *increases* FCR by +0.12 across all babies (p = 0.028). Interesting.
* Weak language x direction interaction. It seems NSE babies have a bigger reversal effect than SE babies? Trying to judge from the heat maps. (p = 0.074). **Before Victoria it was p = 0.098.**


```{r}
fcr_lm <- lmer(fcr ~ age + lang * direction + (1|name) + (1|story), data = babies_fcr)
summary(fcr_lm)
ggcoef(fcr_lm)
```

# Heat Maps
And now heat maps!

```{r}
heatmap_babies <- babies %>%
  filter(aoi %in% midline) %>%
  ungroup() %>%
  group_by(lang, name, direction, aoi) %>%
  summarise(percent = mean(percent, na.rm=TRUE)) %>%
  group_by(lang, direction, aoi) %>%
  summarise(percent = mean(percent, na.rm=TRUE)) %>%
  ungroup() %>%
  mutate(aoi = factor(aoi, levels = c("Belly","BelowChest","MidChestBottom","MidChestCenter","MidChestTop",
            "MidFaceBottom","MidFaceCenter","MidFaceTop")))

ggplot(heatmap_babies, aes(x = lang, y = aoi)) +
  geom_tile(aes(fill=percent),color="lightgray",na.rm=TRUE) + 
#  scale_fill_viridis(option = "viridis", direction=-1, limits = c(0,.7), labels = percent, name = "looking time") +
    scale_fill_gradient(low = "#ffffff", high = "#08519c", space = "Lab", limits = c(0,.41), labels = percent, name = "looking time", na.value = "grey50") +
  theme_bw() +
  theme(strip.text.x = element_text(size = 11, color = "black", face = "italic"), 
        strip.background = element_rect(colour = "white", fill = "white"),
        panel.grid.major = element_line(color = "white")) +
  facet_grid(. ~ direction) +
  ylab("") + xlab("") + ggtitle("Eye Gaze Heat Map, by Direction") + 
  scale_y_discrete(expand=c(0,0)) +
  scale_x_discrete(expand = c(0,0))

ggplot(heatmap_babies, aes(x = direction, y = aoi)) +
  geom_tile(aes(fill=percent),color="lightgray",na.rm=TRUE) + 
#  scale_fill_viridis(option = "viridis", direction=-1, limits = c(0,.7), labels = percent, name = "looking time") +
    scale_fill_gradient(low = "#ffffff", high = "#08519c", space = "Lab", limits = c(0,.41), labels = percent, name = "looking time", na.value = "grey50") +
  theme_bw() +
  theme(strip.text.x = element_text(size = 11, color = "black", face = "italic"), 
        strip.background = element_rect(colour = "white", fill = "white"),
        panel.grid.major = element_line(color = "white")) +
  facet_grid(. ~ lang) +
  ylab("") + xlab("") + ggtitle("Eye Gaze Heat Map, by Language") + 
  scale_y_discrete(expand=c(0,0)) +
  scale_x_discrete(expand = c(0,0))
```

# Different Ways to Visualize Reversal
I want to try to visualize reversal effects a different way. Maybe this. 

```{r}
# Get participant-level data
babies_fcr2 <- babies_fcr %>%
  group_by(name, age, lang, direction) %>%
  summarise(fcr = mean(fcr))

# reversal_effect_lm <- lmer(fcr ~ age + lang * direction + (1|name), data = babies_fcr2)
# summary(reversal_effect_lm)

ggplot(babies_fcr2, aes(x = direction, y = fcr, color = lang, fill = lang)) +
  geom_point() +
  geom_line(aes(group = name)) +
  facet_grid(. ~ lang) + 
  scale_y_continuous(limits = c(-1,1)) +
  theme_bw()

```

Or a reversal effect chart? Okay, so this chart tells us overall there really wasn't much of a reversal effect for SE babies, they're all hovering around 0. Interesting. While there seems to be a reversal effect for NSE babies where they look at the face more during reversed stories! 

```{r}
# Get participant-level data
babies_fcr3 <- babies_fcr2 %>%
  spread(direction, fcr) %>%
  group_by(name, age, lang) %>%
  summarise(diff = forward - reversed)

ggplot(babies_fcr3, aes(x = age, y = diff, color = lang)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  scale_y_continuous(limits = c(-1,1)) +
  theme_bw() +
  ggtitle("Reversal Effect") +
  ylab("Forward FCR - Reversed FCR")
```

This analysis of within-subject variation here: 

```{r}
# First get the mean of each trial, THEN the participant-level means
within_subjects <- babies_fcr %>%
  group_by(name, lang, direction, story, repetition) %>%
  summarise(fcr = mean(fcr, na.rm = TRUE),
            count = n()) %>%
  group_by(name, lang, direction) %>%
  summarise(mean = mean(fcr, na.rm = TRUE),
            se = sd(fcr, na.rm = TRUE)/sqrt(n()),
            count = n())
# Then spread out mean and SE columns by direction
within_subjects_means <- within_subjects %>%
  select(-se, -count) %>%
  spread(direction, mean, sep = "_")
within_subjects_se <- within_subjects %>%
  select(-mean, -count) %>%
  spread(direction, se, sep = "SE")
within_subjects <- left_join(within_subjects_means, within_subjects_se, by = c("name","lang"))

# Now let's plot
lims <- c(-1,1)
within_subjects %>%
  ggplot(aes(x = direction_forward, y = direction_reversed, color = lang)) +
  geom_abline() +
  geom_point(size = 2) + 
  geom_errorbar(aes(ymin=direction_reversed-directionSEreversed, ymax=direction_reversed+directionSEreversed)) +
  geom_errorbarh(aes(xmin=direction_forward-directionSEforward, xmax=direction_forward+directionSEforward)) +
  theme_bw() +
  theme(aspect.ratio = 1) +
  scale_x_continuous("forward", limits = c(-1,1)) +
  scale_y_continuous("reversed", limits = c(-1,1)) +
  ggtitle("FCR Means") +
  facet_wrap("lang")
```

And a classic box/error plot with age collapsed. 

```{r}
babies_fcr2 %>%
  group_by(lang, direction) %>%
  summarise(fcr_mean = mean(fcr),
            sd = sd(fcr),
            n = n(),
            se = sd/sqrt(n)) %>%
  ggplot(aes(x = lang, y = fcr_mean, fill = direction)) +
  geom_bar(stat = "identity", position = position_dodge()) + 
  geom_errorbar(aes(ymin = fcr_mean-se, ymax = fcr_mean+se), position = position_dodge(0.9), width = 0.2) +
  scale_y_continuous(limits = c(-0.5, 0.5)) +
  theme_linedraw()

```

# Discussion re AOI/anatomical data
The biggest change is we lost the interaction between language and direction. For the ICSLA abstract we reported a strong interaction (p = 0.01), but now it's p = 0.10. Likely because of the new babies we added, and recalculating percentages/denominators. 

The interpretation here is that:

* All babies looked equally at all videos regardless of langauge or direction. Good!
* SE babies are stronger face-lookers than NSE babies. (Same as ICSLA)
* Reversal appears to affect NSE babies more than SE babies? (Marginal). This is unlike ICSLA. 

One thing I worry about is using age *without any interactions* and whether people will criticize us for that. Because age x language x direction is a "more complete" model as it suggests age may differently influence various combinations (SE + reversed, NSE + forward, etc) differently, while age + language x direction means we're mainly using age as a covariate, not as a factor of interest. But if we use age as a factor of interest, all significance disappears, so ... we want to use age as a covariate if we want to have a story. But how to defend that decision and not just be p-hacking? I have to think about it... 


```{r eval=FALSE, fig.height=12, fig.width=12, include=FALSE}
# Correlations

# Let's try correlations
babies_nse <- babies %>% 
  filter(aoi %in% midline) %>%
  filter(lang == "NSE") %>%
  group_by(name, direction, aoi) %>% 
  summarise(percent = mean(percent)) %>%
  ungroup() %>%
  mutate(direction = case_when(
    direction == "forward" ~ "fw",
    direction == "reversed" ~ "rv"
  )) %>% 
  unite(aoi2, direction, aoi, sep = "_") %>%
  spread(aoi2, percent) %>%
  select(-name)

babies_se <- babies %>% 
  filter(aoi %in% midline) %>%
  filter(lang == "SE") %>%
  group_by(name, direction, aoi) %>% 
  summarise(percent = mean(percent)) %>%
  ungroup() %>%
  mutate(direction = case_when(
    direction == "forward" ~ "fw",
    direction == "reversed" ~ "rv"
  )) %>% 
  unite(aoi2, direction, aoi, sep = "_") %>%
  spread(aoi2, percent) %>%
  select(-name)

ggcorr(babies_nse, label = TRUE, label_size = 5, label_round = 2, label_alpha = TRUE, hjust = 0.9, size = 5, color = "grey50", layout.exp = 1) + ggtitle("NSE")

ggcorr(babies_se, label = TRUE, label_size = 5, label_round = 2, label_alpha = TRUE, hjust = 0.9, size = 5, color = "grey50", layout.exp = 1) + ggtitle("SE")

library(corrr)
babies_nse %>% correlate() %>% network_plot(min_cor=0.6) + ggtitle("NSE Babies")
babies_se %>% correlate() %>% network_plot(min_cor=0.6) + ggtitle("SE Babies")
```

# XY Space Data
We'll load the data from the `childxydata.feather` file made in 06rawxydata.Rmd. So any new babies, please run the first code block in 06 to include it. Then we'll keep all the babies we also have in the AOI data group. 

```{r message=FALSE, warning=FALSE}
included <- babies %>%
  ungroup() %>%
  select(name) %>% 
  distinct() %>%
  unlist()

xydata <- read_feather("../Child Data/childxydata.feather") %>%
  rename(name = participant) %>%
  filter(name %in% included)

# Get ages
ages <- read_csv("childrenages.csv") %>%
  rename(name = participant)
xydata <- xydata %>% left_join(ages, by = "name") %>%
  mutate(age = age*12) %>%
  mutate(agegroup = case_when(
    age <= 8.99 ~ "younger",
    age >= 9.0 & age < 15 ~ "older"
  )) %>%
  mutate(language = case_when(
    language == "EnglishExposed" ~ "NSE",
    language == "SignLanguageExposed" ~ "SE"
  )) %>%
  rename(lang = language) %>%
  select(name, group, gender, lang, condition, mark, trial, repetition, x, y, age, agegroup) %>%
  separate(condition, into = c("story", "clip", "direction")) %>%
  unite("story", c("story", "clip")) %>%
  mutate(direction = case_when(
    direction == "ER" ~ "reversed",
    direction == "FW" ~ "forward"
  )) %>%
  mutate(name = factor(name),
         group = factor(group),
         gender = factor(gender),
         lang = factor(lang),
         story = factor(story),
         direction = factor(direction),
         mark = factor(mark),
         trial = factor(trial),
         repetition = factor(repetition),
         agegroup = factor(agegroup))
```

## Overall Looking
Let's check that we have no significant group or condition differences in terms of valid (not empty) data points collected. This is same as "Global Looking" we have above, really, but w raw xy data. 

```{r}
xy_overall <- xydata %>%
  filter(!is.na(x)) %>%
  group_by(name, age, lang, direction, story, repetition) %>%
  summarise(data_points = n()) # gets total looking percent for each trial for each baby

# Table of means
xy_overall %>% 
  group_by(name, lang, direction) %>%
  summarise(data_points = mean(data_points)) %>% # get average looking percent for each baby
  group_by(lang, direction) %>%
  summarise(mean_data_points = mean(data_points),
            count = n(),
            sd = sd(data_points),
            se = sd/sqrt(count)) %>%
  select(-sd) %>%
  print()

ggplot(xy_overall, aes(x = age, y = data_points, color = direction, fill = direction)) + 
  geom_jitter(alpha = 0.5) +
  facet_grid(. ~ lang) +
  geom_smooth(method = "lm", se = FALSE) +
  ggtitle("Data Points") +
  xlab("age (months)") +
  ylab("data points recorded") + 
  theme_bw() 
```


A linear model shows there were no significant effects of any factors. We can conclude there was no effect on how *much* data was collected from the babies.   

```{r}
overall_xy_lm <- lmer(data_points ~ age + lang * direction + (direction|name) + (direction|story), data = xy_overall)
summary(overall_xy_lm) 
ggcoef(overall_xy_lm)
```

## XY Data LMMs
Now we're going to run LMMs on babies' raw: 

* horizontal spread (middle 50% of x data; xIQR)
* vertical spread (middle 50% of y data; yIQR)
* viewing area (A = middle-x * middle-y; area)

But to do this we first trim each baby's data, getting rid of the first 60 samples (0.5 secs) of each trial. 

```{r}
xydata <- xydata %>%
  group_by(name,trial) %>%
  slice(60:n())

iqr <- xydata %>%
  group_by(name, age, lang, story, direction, trial) %>%
  summarise(xIQR = IQR(x,na.rm=TRUE),
                   yIQR = IQR(y,na.rm=TRUE),
                   xmed = median(x, na.rm=TRUE),
                   ymed = median(y, na.rm=TRUE),
                   area = xIQR*yIQR)
head(iqr,20)

```


### Middle X

Results tell us that there is a significant effect of age where horizontal spread grew narrower with older babies (p = 0.024; slope = -2.2 px/month). There was a marginal effect of language where SE babies have slightly narrower horizontal spread (11 px; p = 0.088). No effects of reversal or interactions.

```{r}
xiqr_mean <- iqr %>% 
  group_by(lang, direction, name) %>%
  summarise(xIQR = mean(xIQR, na.rm = T)) %>% # gets average looking percent for each baby
  group_by(lang, direction) %>%
  summarise(mean_xIQR = mean(xIQR), # gets group averages
            count = n(),
            sd = sd(xIQR),
            se = sd/sqrt(count)) %>%
  select(-sd) %>%
  print()

# Plot
ggplot(iqr, aes(x = age, y = xIQR, color = direction, fill = direction)) + 
  geom_jitter(alpha = 0.5) + 
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw() + 
  theme(panel.grid.major.x = element_blank()) +
  facet_grid(. ~ lang) +
  ggtitle("Horizontal Spread") +
  xlab("") +
  ylab("xIQR")

ggplot(xiqr_mean, aes(x = lang, y = mean_xIQR, fill = direction)) +
  geom_bar(stat = "identity", position = position_dodge()) + 
  geom_errorbar(aes(ymin = mean_xIQR-se, ymax = mean_xIQR+se), position = position_dodge(0.9), width = 0.2) +
  theme_linedraw()

xiqr_lm <- lmer(xIQR ~ age + lang * direction + (1|name) + (1|story), data = iqr)
summary(xiqr_lm)
ggcoef(xiqr_lm)
```


### Middle Y

We had a significant effect of age where vertical spread got narrower with older babies (p = 0.019, slope = -5.5 px/month). There were no effect of language, direction, or interactions. 

```{r}
yiqr_mean <- iqr %>% 
  group_by(lang, direction, name) %>%
  summarise(yIQR = mean(yIQR, na.rm = T)) %>% # gets average looking percent for each baby
  group_by(lang, direction) %>%
  summarise(mean_yIQR = mean(yIQR), # gets group averages
            count = n(),
            sd = sd(yIQR),
            se = sd/sqrt(count)) %>%
  select(-sd) %>%
  print()

# Plot
ggplot(iqr, aes(x = age, y = yIQR, color = direction, fill = direction)) + 
  geom_jitter(alpha = 0.5) + 
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw() + 
  theme(panel.grid.major.x = element_blank()) +
  facet_grid(. ~ lang) +
  ggtitle("Vertical Spread") +
  xlab("") +
  ylab("yIQR")

ggplot(yiqr_mean, aes(x = lang, y = mean_yIQR, fill = direction)) +
  geom_bar(stat = "identity", position = position_dodge()) + 
  geom_errorbar(aes(ymin = mean_yIQR-se, ymax = mean_yIQR+se), position = position_dodge(0.9), width = 0.2) +
  theme_linedraw()

yiqr_lm <- lmer(yIQR ~ age + lang * direction + (1|name) + (1|story), data = iqr)
summary(yiqr_lm)
ggcoef(yiqr_lm)
```

### Viewing Area
Again, age is significant (p = 0.01) such that area gets smaller with age (about 500 sq. px. per month). No effect of language or direction or interactions. 

```{r}
area_mean <- iqr %>% 
  group_by(lang, direction, name) %>%
  summarise(area = mean(area, na.rm = T)) %>% # gets average looking percent for each baby
  group_by(lang, direction) %>%
  summarise(area_mean = mean(area), # gets group averages
            count = n(),
            sd = sd(area),
            se = sd/sqrt(count)) %>%
  select(-sd) %>%
  print()

# Plot
ggplot(iqr, aes(x = age, y = area, color = direction, fill = direction)) + 
  geom_jitter(alpha = 0.5) + 
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw() + 
  theme(panel.grid.major.x = element_blank()) +
  facet_grid(. ~ lang) +
  ggtitle("Viewing Area") +
  xlab("") +
  ylab("Area (px^2)")

ggplot(area_mean, aes(x = lang, y = area_mean, fill = direction)) +
  geom_bar(stat = "identity", position = position_dodge()) + 
  geom_errorbar(aes(ymin = area_mean-se, ymax = area_mean+se), position = position_dodge(0.9), width = 0.2) +
  theme_linedraw()

area_lm <- lmer(area ~ age + lang * direction + (1|name) + (1|story), data = iqr)
summary(area_lm)
ggcoef(area_lm)
```

## Plotting Viewing Area 

```{r}
medians <- iqr %>%
  group_by(name,lang,direction) %>%
  summarise(xIQR = median(xIQR,na.rm=TRUE),
                   yIQR = median(yIQR,na.rm=TRUE),
                   xmed = median(xmed,na.rm=TRUE),
                   ymed = median(ymed,na.rm=TRUE)) %>%
  group_by(lang,direction) %>% 
  summarise(xIQR = median(xIQR,na.rm=TRUE),
                   yIQR = median(yIQR,na.rm=TRUE),
                   x = median(xmed,na.rm=TRUE),
                   y = median(ymed,na.rm=TRUE)) %>%
  mutate(y = y*-1,
         xmin = x-(xIQR/2),
         xmax = x+(xIQR/2),
         ymin = y-(yIQR/2),
         ymax = y+(yIQR/2))
img <- png::readPNG("cindy.png")
g <- grid::rasterGrob(img, interpolate=TRUE, width=unit(1,"npc"), height=unit(1,"npc")) 
ggplot(medians, aes(fill=direction,color=direction)) +
  annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
  geom_rect(aes(xmin=xmin,ymin=ymin,xmax=xmax,ymax=ymax),alpha=.1) + 
  theme_linedraw() +
  scale_x_continuous(limits = c(0,1080), expand = c(0, 0)) +
  scale_y_continuous(limits = c(-720,0), expand = c(0, 0)) +
  facet_wrap("lang")
```

