---
title: "Children - Study 2 - Results"
output: 
  html_notebook:
    code_folding: hide
    theme: spacelab
    highlight: tango
    toc: yes
    toc_depth: 2
    toc_float: yes
    df_print: paged
---

This is the results section for the Study 2 NSE & SE CHILDREN watching ASL Stories. We have two main factors: 

1. Language (Sign v. English)
1. Direction (Forward v. Reversed)

We are taking out one older KODA (Ethan, 10.5 yrs) to balance the groups better. 

# Demographics
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(janitor)
library(lme4)
library(lmerTest)
library(scales)
library(feather)
library(GGally)

kids <- read_feather("cleanedchildeyedata.feather") %>%
#  mutate(age = age*12) %>%
  select(participant, language, age, gender, story, direction, mark, trial, repetition, aoi, secs, percent) %>%
  rename(name = participant) %>%
  filter(age < 9) %>% # Take out Ethan
  # mutate(agegroup = case_when(
  #   age <= 8.99 ~ "younger",
  #   age >= 9.0 & age < 15 ~ "older"
  # )) %>%
  # filter(!is.na(agegroup)) %>%
  mutate(language = case_when(
    language == "english" ~ "NSE",
    language =="sign" ~ "SE"
  )) %>%
  rename(lang = language)

kidsinfo <- kids %>%
  select(name, lang, age, gender) %>%
  distinct() %>%
  group_by(lang) %>%
  summarise(N = n(),
            age_mean = mean(age),
            sd = sd(age),
            min = min(age),
            max = max(age))

genders <- kids %>%
  select(name, lang, age, gender) %>%
  distinct() %>%
  group_by(lang, gender) %>%
  summarise(N = n()) %>%
  spread(gender, N)

kidsinfo <- left_join(kidsinfo, genders) %>%
  select(lang, N, Female, Male, age_mean, sd, min, max) %>%
  print()

# babies$agegroup <- fct_relevel(babies$agegroup, c("younger","older"))


# IF we do age groups, use this code
# 
# babiesinfo <- babies %>%
#   select(name, lang, age, agegroup, gender) %>%
#   distinct() %>%
#   group_by(lang, agegroup) %>%
#   summarise(N = n(),
#             age_mean = mean(age),
#             sd = sd(age),
#             min = min(age),
#             max = max(age))
# 
# genders <- babies %>%
#   select(name, lang, age, agegroup, gender) %>%
#   distinct() %>%
#   group_by(lang, agegroup, gender) %>%
#   summarise(N = n()) %>%
#   spread(gender, N)
# 
# babiesinfo <- left_join(babiesinfo, genders) %>%
#   select(lang, agegroup, N, Female, Male, age_mean, sd, min, max) %>%
#   print()
```

Let's plot the ages, and check if there is significant difference in ages between the two groups?

```{r}
# Boxplot
kids %>%
  select(name, age, lang) %>%
  distinct() %>%
  ggplot(aes(x = lang, y = age, fill = lang)) + geom_boxplot(width = 0.5) + guides(fill = FALSE)

kids %>%
  select(name, age, lang) %>%
  distinct() %>%
  ggplot(aes(x = age, fill = lang)) + geom_histogram() + facet_grid(lang ~ .)


# T-test
nse_age <- kids %>% filter(lang == "NSE") %>% select(name, age) %>% distinct()
se_age <- kids %>% filter(lang == "SE") %>% select(name, age) %>% distinct()
t.test(nse_age$age, se_age$age)
```


# Global Looking

For children, we calculated percentages *based on overall clip length* as the denominator. In this way, we can meaningfully contrast looking times at the videos (which are variable lengths) based on different factors. But when we go to AOI analysis we need to re-calculate the percentages so the denominator is based on total looking time, not overall clip length. 

The chart below shows there seems to be an effect of age; older kids look longer at it than younger kids. Maybe not too surprising. It means we need to keep age in any models we run. Let's analyze a bit more below.

```{r}
kids$lang <- as.factor(kids$lang)
kids_overall_looking <- kids %>%
  group_by(name, age, lang, direction, story, repetition) %>%
  summarise(percent = sum(percent)) # gets total looking percent for each trial for each kid

# Table of means
kids_overall_looking %>% 
  group_by(name, lang, direction) %>%
  summarise(percent = mean(percent)) %>% # get average looking percent for each kid
  group_by(lang, direction) %>%
  summarise(mean_percent = mean(percent),
            count = n(),
            sd = sd(percent),
            se = sd/sqrt(count)) %>%
  select(-sd) %>%
  print()

ggplot(kids_overall_looking, aes(x = age, y = percent, color = direction, fill = direction)) + 
  geom_jitter(alpha = 0.5) +
  facet_grid(. ~ lang) +
  geom_smooth(method = "lm", se = TRUE) +
  ggtitle("Video Attention") +
  xlab("age (months)") +
  ylab("percent looking") + 
  theme_bw() + 
  scale_y_continuous(limits = c(0,1), labels = percent) 


# Plot
# babies_overall_looking %>% 
#   group_by(lang, direction, name) %>%
#   summarise(percent = mean(percent)) %>% # gets average looking percent for each baby
#   group_by(lang, direction) %>%
#   summarise(mean_percent = mean(percent), # gets group averages
#             count = n(),
#             sd = sd(percent),
#             se = sd/sqrt(count)) %>% 
#   ggplot(aes(x = lang, y = mean_percent, fill = direction)) + 
#   geom_col(position = "dodge") + 
#   geom_errorbar(aes(ymin = mean_percent - se, ymax = mean_percent + se), 
#                 position = position_dodge(width = 0.9), width = 0.25) + 
#   scale_y_continuous(limits = c(0,1), labels = percent) +
#   theme_minimal() + 
#   theme(panel.grid.major.x = element_blank()) +
# #  facet_wrap("lang") +
#   ggtitle("Video Attention") +
#   xlab("") +
#   ylab("percent looking")

# babies_overall_looking %>%
#   ggplot(aes(x = lang, y = percent, fill = direction)) +
#   facet_wrap("agegroup") + 
#   geom_violin()
```

A linear model shows a significant effect of age. Overall, Age seems to increase overall looking by about 3% every year. However, there are no differences between NSE v. SE, or reversal, on how long they looked, so that's good. 

```{r}
global_lm <- lmer(percent ~ age + lang * direction + (1|name) + (1|story), data = kids_overall_looking)
summary(global_lm)
confint(global_lm)
#ggcoef(global_lm)
```

# AOI Looking
Now we'll re-calculate the percentages so the denominator is based on total looking time. All AOIs should sum up to 100% for each trial and each baby. Next let's make a boxplot of all AOIs. Interesting, definitely more MidFaceBottom focus here than we had with babies, but also more distribution too.

```{r}
# Recalculate percent
kids <- kids %>% 
  ungroup() %>%
  select(-percent) %>%
  group_by(name, lang, age, direction, story, mark, trial, repetition, gender) %>%
  mutate(totalsec = sum(secs)) %>%
  group_by(name, lang, age, direction, story, mark, trial, repetition, gender, aoi) %>%
  summarise(percent = secs/totalsec)

# Boxplot
kids %>%
  ggplot(aes(x = aoi, y = percent, fill = direction)) + 
  geom_boxplot() +
  ggtitle("AOI Attention") +
  theme_bw() + 
  xlab("") +
  theme(axis.text.x = element_text(angle=45, hjust = 1),
        panel.grid.major.x = element_blank()) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1))
```
It appears two important AOIs are MidChestTop and MidFaceBottom. Let's look again only at midline AOIs:

```{r}
midline = c("Belly","BelowChest","MidChestBottom","MidChestCenter","MidChestTop",
            "MidFaceBottom","MidFaceCenter","MidFaceTop")
kids %>%
  filter(aoi %in% midline) %>%
  ggplot(aes(x = aoi, y = percent, fill = direction)) + 
  geom_boxplot() +
  ggtitle("Midline AOI Attention") +
  theme_bw() + 
  xlab("") +
  theme(axis.text.x = element_text(angle=45, hjust = 1),
        panel.grid.major.x = element_blank()) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1))
```

I'm going to run linear models with only MidChestTop or MidFaceBottom, and see what happens. No age interactions.

**MidChestTop:**

* No effect of age.
* No effect of language.
* *Weak* effect of direction (p = 0.084) - reversed means they look ~ 4.7% less at midchesttop.
* No language X direction interaction. 


**MidFaceBottom:** 

* No effect of age.
* Significant effect of language (p = 0.004) - SE look at MidFaceBottom +19% more than NSE children
* No effect of direction.
* No language X direction interaction.


```{r}
kids %>%
  filter(aoi %in% c("MidFaceBottom","MidChestTop")) %>%
  ggplot(aes(x = age, y = percent, color = direction, fill = direction)) + 
  geom_jitter(alpha = 0.5) + 
  geom_smooth(method = "lm", se = FALSE) +
  scale_y_continuous(limits = c(0,1), labels = percent) +
  theme_bw() + 
#  theme(panel.grid.major.x = element_blank()) +
  facet_grid(aoi ~ lang) +
  ggtitle("AOI Attention") +
  xlab("") +
  ylab("percent looking")

midchesttop_lm <- lmer(percent ~ age + lang * direction + (1|name) + (1|story), data = filter(kids, aoi == "MidChestTop"))
summary(midchesttop_lm)
confint(midchesttop_lm)
#ggcoef(midchesttop_lm)

midfacebottom_lm <- lmer(percent ~ age + lang * direction + (1|name) + (1|story), data = filter(kids, aoi == "MidFaceBottom"))
summary(midfacebottom_lm)
confint(midfacebottom_lm)
#ggcoef(midfacebottom_lm)

# Bar chart
# babies %>%
#   filter(aoi %in% c("MidFaceBottom","MidChestTop")) %>%
#   group_by(agegroup, lang, direction, name, aoi) %>%
#   summarise(percent = mean(percent)) %>% # gets average looking percent for each baby
#   group_by(agegroup, lang, direction, aoi) %>%
#   summarise(mean_percent = mean(percent), # gets group averages
#             count = n(),
#             sd = sd(percent),
#             se = sd/sqrt(count)) %>% 
#   ggplot(aes(x = lang, y = mean_percent, fill = direction)) + 
#   geom_col(position = "dodge") + 
#   geom_errorbar(aes(ymin = mean_percent - se, ymax = mean_percent + se), 
#                 position = position_dodge(width = 0.9), width = 0.25) + 
#   scale_y_continuous(limits = c(0,1), labels = percent) +
#   theme_minimal() + 
#   theme(panel.grid.major.x = element_blank()) +
#   facet_grid(aoi ~ agegroup) +
#   ggtitle("Video Attention") +
#   xlab("") +
#   ylab("percent looking")
```


# Face-Chest Ratio
Next, we'll define a Face-Chest Ratio (FCR) such that:

1. MidFaceCenter, MidFaceBottom = Face
1. MidChestTop, MidChestCenter, MidChestBottom, BelowChest = Chest
1. FCR = face - chest / face + chest

We did not include Belly or MidFaceTop because of very low looking rates according to the boxplots above.

```{r}
kids_fcr <- kids %>%
  ungroup() %>%
  spread(aoi,percent) %>%
  group_by(name, age, lang, gender, direction, story, repetition) %>%
  summarise(face = sum(MidFaceCenter, MidFaceBottom, na.rm = TRUE),
         chest = sum(MidChestTop, MidChestCenter, MidChestBottom, BelowChest, na.rm = TRUE),
         fcr = (face - chest) / (face + chest))

# Table of means
kids_fcr %>% 
  group_by(lang, direction, name) %>%
  summarise(fcr = mean(fcr)) %>% # gets average looking percent for each baby
  group_by(lang, direction) %>%
  summarise(mean_fcr = mean(fcr), # gets group averages
            count = n(),
            sd = sd(fcr),
            se = sd/sqrt(count)) %>%
  select(-sd) %>%
  print()

# Plot
ggplot(kids_fcr, aes(x = age, y = fcr, color = direction, fill = direction)) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_jitter(alpha = 0.5) + 
  geom_smooth(method = "lm", se = FALSE) +
  scale_y_continuous(limits = c(-1,1)) +
  theme_bw() + 
  theme(panel.grid.major.x = element_blank()) +
  facet_grid(. ~ lang) +
  ggtitle("Face-Chest Ratios") +
  xlab("") +
  ylab("FCR")

# Bar chart
# babies_fcr %>% 
#   group_by(agegroup, lang, direction, name) %>%
#   summarise(fcr = mean(fcr)) %>% # gets average looking percent for each baby
#   group_by(agegroup, lang, direction) %>%
#   summarise(mean_fcr = mean(fcr), # gets group averages
#             count = n(),
#             sd = sd(fcr),
#             se = sd/sqrt(count)) %>% 
#   ggplot(aes(x = lang, y = mean_fcr, fill = direction)) + 
#   geom_col(position = "dodge") + 
#   geom_errorbar(aes(ymin = mean_fcr - se, ymax = mean_fcr + se), 
#                 position = position_dodge(width = 0.9), width = 0.25) + 
#   scale_y_continuous(limits = c(-1,1)) +
#   theme_minimal() + 
#   theme(panel.grid.major.x = element_blank()) +
#   facet_wrap("agegroup") +
#   ggtitle("Face-Chest Ratios") +
#   xlab("") +
#   ylab("FCR")
```

What will a linear mixed model tell us? (with no age interactions)

* No effect of age. Interesting. Maybe just becuase we don't have that many babies. 
* Effect of language: SE babies have overall +0.36 FCR than NSE babies (p = 0.03). SE looks at the face more than the chest. 
* No effect of direction. Interesting. 
* No interaction. Interesting. 

```{r}
fcr_lm <- lmer(fcr ~ age + lang * direction + (1|name) + (1|story), data = kids_fcr)
summary(fcr_lm)
confint(fcr_lm)
#ggcoef(fcr_lm)
```

# The Large Table

> I would like a large table with all individual percent looking means for each AOI and the individual FCR values, with ages, gender, video group for each child.  (collapsed across stories and trials)  

```{r message=FALSE, warning=FALSE}
# Collapse across stories and trials 

kids_spread <- kids %>%
  group_by(name, lang, age, gender, direction, aoi) %>%
  summarise(percent = mean(percent, na.rm = T)) %>%
  spread(aoi, percent)

kids_fcr_spread <- kids_fcr %>%
  group_by(name, lang, age, gender, direction) %>%
  summarise(fcr = mean(fcr, na.rm = T))

kids_large_table <- kids_spread %>%
  left_join(kids_fcr_spread)

kids_large_table %>%
  write_csv("large_table_kids.csv")
```


# Visualizing Reversal Effect
I want to try to visualize reversal effects a different way. Maybe this. 

```{r}
# Get participant-level data
kids_fcr2 <- kids_fcr %>%
  group_by(name, age, lang, direction) %>%
  summarise(fcr = mean(fcr))

# reversal_effect_lm <- lmer(fcr ~ age + lang * direction + (1|name), data = kids_fcr2)
# summary(reversal_effect_lm)

ggplot(kids_fcr2, aes(x = direction, y = fcr, color = lang, fill = lang)) +
  geom_point() +
  geom_line(aes(group = name)) +
  facet_grid(. ~ lang) + 
  scale_y_continuous(limits = c(-1,1)) +
  theme_bw()

```

Or a reversal effect chart? Okay, so this chart tells us overall there really wasn't much of a reversal effect for SE babies, they're all hovering around 0. Interesting. While there seems to be a reversal effect for NSE babies where they look at the face more during reversed stories! 

```{r}
# Get participant-level data
kids_fcr3 <- kids_fcr2 %>%
  spread(direction, fcr) %>%
  group_by(name, age, lang) %>%
  mutate(diff = forward - reversed)

ggplot(kids_fcr3, aes(x = age, y = diff, color = lang)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  scale_y_continuous(limits = c(-1,1)) +
  theme_bw() +
  ggtitle("Reversal Effect") +
  ylab("Forward FCR - Reversed FCR")
```

And within-subjects variation here: 

```{r}
# First get the mean of each trial, THEN the participant-level means
within_subjects <- kids_fcr %>%
  group_by(name, lang, direction, story, repetition) %>%
  summarise(fcr = mean(fcr, na.rm = TRUE),
            count = n()) %>%
  group_by(name, lang, direction) %>%
  summarise(mean = mean(fcr, na.rm = TRUE),
            se = sd(fcr, na.rm = TRUE)/sqrt(n()),
            count = n())
# Then spread out mean and SE columns by direction
within_subjects_means <- within_subjects %>%
  select(-se, -count) %>%
  spread(direction, mean, sep = "_")
within_subjects_se <- within_subjects %>%
  select(-mean, -count) %>%
  spread(direction, se, sep = "SE")
within_subjects <- left_join(within_subjects_means, within_subjects_se, by = c("name","lang"))

# Now let's plot
lims <- c(-1,1)
within_subjects %>%
  ggplot(aes(x = direction_forward, y = direction_reversed, color = lang)) +
    geom_abline() +
  geom_point(size = 2) + 
  geom_errorbar(aes(ymin=direction_reversed-directionSEreversed, ymax=direction_reversed+directionSEreversed)) +
  geom_errorbarh(aes(xmin=direction_forward-directionSEforward, xmax=direction_forward+directionSEforward)) +
  theme_bw() +
  theme(aspect.ratio = 1) +
  scale_x_continuous("forward", limits = c(-1,1)) +
  scale_y_continuous("reversed", limits = c(-1,1)) +
  ggtitle("FCR Means") +
  facet_wrap("lang")
```

And a classic box/error plot with age collapsed. 

```{r}
kids_fcr2 %>%
  group_by(lang, direction) %>%
  summarise(fcr_mean = mean(fcr),
            sd = sd(fcr),
            n = n(),
            se = sd/sqrt(n)) %>%
  ggplot(aes(x = lang, y = fcr_mean, fill = direction)) +
  geom_bar(stat = "identity", position = position_dodge()) + 
  geom_errorbar(aes(ymin = fcr_mean-se, ymax = fcr_mean+se), position = position_dodge(0.9), width = 0.2) +
  scale_y_continuous(limits = c(-0.5, 0.5)) +
  theme_linedraw()

```

```{r fig.width=6.5, fig.height=6}

library(extrafont)

kids_fcr2 %>%
  group_by(lang, direction) %>%
  summarise(fcr_mean = mean(fcr),
            sd = sd(fcr),
            n = n(),
            se = sd/sqrt(n)) %>%
  ggplot(aes(x = lang, y = fcr_mean, color = direction, fill = direction, group = direction)) +
  geom_hline(yintercept = 0, size = 0.5) +
  geom_point(size = 6, position = position_dodge(width = 0.4)) +
  geom_errorbar(aes(ymin = fcr_mean-se, ymax = fcr_mean+se), 
                size = 2, 
                position = position_dodge(0.4), 
                width = 0.3) +
  scale_y_continuous(limits = c(-0.5, 0.5)) +
  theme_linedraw() +
  theme(text = element_text(size = 30),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.border = element_rect(size = 2),
        axis.ticks.y = element_line(size = 0.5),
        panel.grid.major.y = element_line(size = 0.5, color = "light gray", linetype = "dashed")) +
  guides(color = FALSE, fill = FALSE)

```

# Heat Maps
And now heat maps!

```{r}
heatmap_kids <- kids %>%
  filter(aoi %in% midline) %>%
  ungroup() %>%
  group_by(lang, name, direction, aoi) %>%
  summarise(percent = mean(percent, na.rm=TRUE)) %>%
  group_by(lang, direction, aoi) %>%
  summarise(percent = mean(percent, na.rm=TRUE)) %>%
  ungroup() %>%
  mutate(aoi = factor(aoi, levels = c("Belly","BelowChest","MidChestBottom","MidChestCenter","MidChestTop",
            "MidFaceBottom","MidFaceCenter","MidFaceTop")))

ggplot(heatmap_kids, aes(x = lang, y = aoi)) +
  geom_tile(aes(fill=percent),color="lightgray",na.rm=TRUE) + 
#  scale_fill_viridis(option = "viridis", direction=-1, limits = c(0,.7), labels = percent, name = "looking time") +
    scale_fill_gradient(low = "#ffffff", high = "#08519c", space = "Lab", limits = c(0,.52), labels = percent, name = "looking time", na.value = "grey50") +
  theme_bw() +
  theme(strip.text.x = element_text(size = 11, color = "black", face = "italic"), 
        strip.background = element_rect(colour = "white", fill = "white"),
        panel.grid.major = element_line(color = "white")) +
  facet_grid(. ~ direction) +
  ylab("") + xlab("") + ggtitle("Eye Gaze Heat Map, by Direction") + 
  scale_y_discrete(expand=c(0,0)) +
  scale_x_discrete(expand = c(0,0))

ggplot(heatmap_kids, aes(x = direction, y = aoi)) +
  geom_tile(aes(fill=percent),color="lightgray",na.rm=TRUE) + 
#  scale_fill_viridis(option = "viridis", direction=-1, limits = c(0,.7), labels = percent, name = "looking time") +
    scale_fill_gradient(low = "#ffffff", high = "#08519c", space = "Lab", limits = c(0,.52), labels = percent, name = "looking time", na.value = "grey50") +
  theme_bw() +
  theme(strip.text.x = element_text(size = 11, color = "black", face = "italic"), 
        strip.background = element_rect(colour = "white", fill = "white"),
        panel.grid.major = element_line(color = "white")) +
  facet_grid(. ~ lang) +
  ylab("") + xlab("") + ggtitle("Eye Gaze Heat Map, by Language") + 
  scale_y_discrete(expand=c(0,0)) +
  scale_x_discrete(expand = c(0,0))
```


## Collaped by direction (new)
```{r}
heatmap_kids2 <- kids %>%
  filter(aoi %in% midline) %>%
  ungroup() %>%
  group_by(lang, name, aoi) %>%
  summarise(percent = mean(percent, na.rm=TRUE)) %>%
  group_by(lang, aoi) %>%
  summarise(percent = mean(percent, na.rm=TRUE)) %>%
  ungroup() %>%
  mutate(aoi = factor(aoi, levels = c("Belly","BelowChest","MidChestBottom","MidChestCenter","MidChestTop",
            "MidFaceBottom","MidFaceCenter","MidFaceTop")))

ggplot(heatmap_kids2, aes(x = lang, y = aoi)) +
  geom_tile(aes(fill=percent),color="lightgray",na.rm=TRUE) + 
#  scale_fill_viridis(option = "viridis", direction=-1, limits = c(0,.7), labels = percent, name = "looking time") +
    scale_fill_gradient(low = "#ffffff", high = "#08519c", space = "Lab", limits = c(0,.52), labels = percent, name = "looking time", na.value = "grey50") +
  theme_bw() +
  theme(strip.text.x = element_text(size = 11, color = "black", face = "italic"), 
        strip.background = element_rect(colour = "white", fill = "white"),
        panel.grid.major = element_line(color = "white")) +
  ylab("") + xlab("") + ggtitle("Eye Gaze Heat Map, by Language (Collapsed by Direction") + 
  scale_y_discrete(expand=c(0,0)) +
  scale_x_discrete(expand = c(0,0))
```


## For poster? 
```{r fig.width = 6.5, fig.height = 6}
ggplot(heatmap_kids, aes(x = direction, y = aoi)) +
  geom_tile(aes(fill=percent), 
            color="dark gray", 
            size = 0.25, 
            na.rm=T, 
            height = rep(c(10,4,1,1,1,1,1,1),4)
            ) + 
  scale_fill_gradient(low = "#ffffff", 
                      high = "#08519c", 
                      space = "Lab", 
                      limits = c(0,.52), 
                      labels = percent, 
                      name = "looking time", 
                      na.value = "grey50") +
  facet_grid(. ~ lang) +
  ylab("") + xlab("") + ggtitle("Eye Gaze Heat Map, by Language") + 
  scale_y_discrete(expand=c(0,0)) +
  scale_x_discrete(expand=c(0,0)) +
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        strip.text = element_blank(),
        panel.border = element_rect(size = 2),
        title = element_blank()) + 
  guides(color = FALSE, fill = FALSE)
```




```{r}
# All Data
#Here's all AOI data. 

kids %>%
  ungroup() %>%
  group_by(lang, name, direction, aoi) %>%
  summarise(percent = mean(percent, na.rm=TRUE)) %>%
  group_by(lang, direction, aoi) %>%
  summarise(percent = mean(percent, na.rm=TRUE)) %>%
  openxlsx::write.xlsx("~/Desktop/kids_by_direction.xlsx")

kids %>%
  ungroup() %>%
  group_by(lang, name, direction, aoi) %>%
  summarise(percent = mean(percent, na.rm=TRUE)) %>%
  group_by(lang, direction, aoi) %>%
  summarise(percent = mean(percent, na.rm=TRUE)) %>%
  group_by(lang, aoi) %>%
  summarise(percent = mean(percent, na.rm=TRUE)) %>%
  openxlsx::write.xlsx("~/Desktop/kids_collapsed.xlsx")
```

# Discussion
No big changes from the ICSLA abstract. Good! 

The interpretation here is that:

* All kids looked equally at all videos regardless of language or direction. Age did have an effect so we used age in our models. Good!
* SE kids continue to be strong face-lookers compared to NSE kids.  (Same as ICSLA)
* There is no reversal effect. (Same as ICSLA)

That doesn't mean both groups of children don't care about reversal. On the contrary. We can hypothesize that SE kids have efficient gaze behavior and are resilient to reversal; while NSE kids already are "inefficient" and changing the video stimulus isn't going to help. But how do we test that? Maybe let's look at within-subject variation.

# Correlations
Let's try correlations.
```{r fig.height=12, fig.width=12}
# Let's try correlations
kids_nse <- kids %>% 
  filter(aoi %in% midline) %>%
  filter(lang == "NSE") %>%
  group_by(name, direction, aoi) %>% 
  summarise(percent = mean(percent)) %>%
  ungroup() %>%
  mutate(direction = case_when(
    direction == "forward" ~ "fw",
    direction == "reversed" ~ "rv"
  )) %>% 
  unite(aoi2, direction, aoi, sep = "_") %>%
  spread(aoi2, percent) %>%
  select(-name)

kids_se <- kids %>% 
  filter(aoi %in% midline) %>%
  filter(lang == "SE") %>%
  group_by(name, direction, aoi) %>% 
  summarise(percent = mean(percent)) %>%
  ungroup() %>%
  mutate(direction = case_when(
    direction == "forward" ~ "fw",
    direction == "reversed" ~ "rv"
  )) %>% 
  unite(aoi2, direction, aoi, sep = "_") %>%
  spread(aoi2, percent) %>%
  select(-name)

ggcorr(kids_nse, label = TRUE, label_size = 5, label_round = 2, label_alpha = TRUE, hjust = 0.9, size = 5, color = "grey50", layout.exp = 1) + ggtitle("NSE")

ggcorr(kids_se, label = TRUE, label_size = 5, label_round = 2, label_alpha = TRUE, hjust = 0.9, size = 5, color = "grey50", layout.exp = 1) + ggtitle("SE")

library(corrr)
kids_nse %>% correlate() %>% network_plot(min_cor=0.6) + ggtitle("NSE Children")
kids_se %>% correlate() %>% network_plot(min_cor=0.6) + ggtitle("SE Children")

```

# XY Space Data
We'll load the data from the `childxydata.feather` file made in 06rawxydata.Rmd. So any new kids, please run the first code block in 06 to include it. Then we'll keep all the kids we also have in the AOI data group. 

```{r message=FALSE, warning=FALSE}
included <- kids %>%
  ungroup() %>%
  select(name) %>% 
  distinct() %>%
  unlist()

xydata <- read_feather("../Child Data/childxydata.feather") %>%
  rename(name = participant) %>%
  filter(name %in% included)

# Get ages
ages <- read_csv("childrenages.csv") %>%
  rename(name = participant)
xydata <- xydata %>% left_join(ages, by = "name") %>%
  mutate(age = age*12) %>%
  mutate(agegroup = case_when(
    age <= 8.99 ~ "younger",
    age >= 9.0 & age < 15 ~ "older"
  )) %>%
  mutate(language = case_when(
    language == "EnglishExposed" ~ "NSE",
    language == "SignLanguageExposed" ~ "SE"
  )) %>%
  rename(lang = language) %>%
  select(name, group, gender, lang, condition, mark, trial, repetition, x, y, age, agegroup) %>%
  separate(condition, into = c("story", "clip", "direction")) %>%
  unite("story", c("story", "clip")) %>%
  mutate(direction = case_when(
    direction == "ER" ~ "reversed",
    direction == "FW" ~ "forward"
  )) %>%
  mutate(name = factor(name),
         group = factor(group),
         gender = factor(gender),
         lang = factor(lang),
         story = factor(story),
         direction = factor(direction),
         mark = factor(mark),
         trial = factor(trial),
         repetition = factor(repetition),
         agegroup = factor(agegroup))
```

## Overall Looking
Let's check that we have no significant group or condition differences in terms of valid (not empty) data points collected. This is same as "Global Looking" we have above, really, but w raw xy data. 

```{r}
xy_overall <- xydata %>%
  filter(!is.na(x)) %>%
  group_by(name, age, lang, direction, story, repetition) %>%
  summarise(data_points = n()) # gets total looking percent for each trial for each baby

# Table of means
xy_overall %>% 
  group_by(name, lang, direction) %>%
  summarise(data_points = mean(data_points)) %>% # get average looking percent for each baby
  group_by(lang, direction) %>%
  summarise(mean_data_points = mean(data_points),
            count = n(),
            sd = sd(data_points),
            se = sd/sqrt(count)) %>%
  select(-sd) %>%
  print()

ggplot(xy_overall, aes(x = age, y = data_points, color = direction, fill = direction)) + 
  geom_jitter(alpha = 0.5) +
  facet_grid(. ~ lang) +
  geom_smooth(method = "lm", se = FALSE) +
  ggtitle("Data Points") +
  xlab("age (months)") +
  ylab("data points recorded") + 
  theme_bw() 
```


Description.

```{r}
overall_xy_lm <- lmer(data_points ~ age + lang * direction + (direction|name) + (direction|story), data = xy_overall)
summary(overall_xy_lm) 
confint(overall_xy_lm)
#ggcoef(overall_xy_lm)
```

## XY Data LMMs
Now we're going to run LMMs on babies' raw: 

* horizontal spread (middle 50% of x data; xIQR)
* vertical spread (middle 50% of y data; yIQR)
* viewing area (A = middle-x * middle-y; area)

But to do this we first trim each kid's data, getting rid of the first 60 samples (0.50 secs) of each trial. 

```{r}
xydata <- xydata %>%
  group_by(name,trial) %>%
  slice(30:n())

iqr <- xydata %>%
  group_by(name, age, lang, story, direction, trial) %>%
  summarise(xIQR = IQR(x,na.rm=TRUE),
                   yIQR = IQR(y,na.rm=TRUE),
                   xmed = median(x, na.rm=TRUE),
                   ymed = median(y, na.rm=TRUE),
                   area = xIQR*yIQR)
head(iqr,20)

```


### Middle X
Description.

```{r}
xiqr_mean <- iqr %>% 
  group_by(lang, direction, name) %>%
  summarise(xIQR = mean(xIQR, na.rm = T)) %>% # gets average looking percent for each baby
  group_by(lang, direction) %>%
  summarise(mean_xIQR = mean(xIQR), # gets group averages
            count = n(),
            sd = sd(xIQR),
            se = sd/sqrt(count)) %>%
  select(-sd) %>%
  print()

# Plot
ggplot(iqr, aes(x = age, y = xIQR, color = direction, fill = direction)) + 
  geom_jitter(alpha = 0.5) + 
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw() + 
  theme(panel.grid.major.x = element_blank()) +
  facet_grid(. ~ lang) +
  ggtitle("Horizontal Spread") +
  xlab("") +
  ylab("xIQR")

ggplot(xiqr_mean, aes(x = lang, y = mean_xIQR, fill = direction)) +
  geom_bar(stat = "identity", position = position_dodge()) + 
  geom_errorbar(aes(ymin = mean_xIQR-se, ymax = mean_xIQR+se), position = position_dodge(0.9), width = 0.2) +
  theme_linedraw()

xiqr_lm <- lmer(xIQR ~ age + lang * direction + (1|name) + (1|story), data = iqr)
summary(xiqr_lm)
confint(xiqr_lm)
#ggcoef(xiqr_lm)
```


### Middle Y
Description.

```{r}
yiqr_mean <- iqr %>% 
  group_by(lang, direction, name) %>%
  summarise(yIQR = mean(yIQR, na.rm = T)) %>% # gets average looking percent for each baby
  group_by(lang, direction) %>%
  summarise(mean_yIQR = mean(yIQR), # gets group averages
            count = n(),
            sd = sd(yIQR),
            se = sd/sqrt(count)) %>%
  select(-sd) %>%
  print()

# Plot
ggplot(iqr, aes(x = age, y = yIQR, color = direction, fill = direction)) + 
  geom_jitter(alpha = 0.5) + 
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw() + 
  theme(panel.grid.major.x = element_blank()) +
  facet_grid(. ~ lang) +
  ggtitle("Vertical Spread") +
  xlab("") +
  ylab("yIQR")

ggplot(yiqr_mean, aes(x = lang, y = mean_yIQR, fill = direction)) +
  geom_bar(stat = "identity", position = position_dodge()) + 
  geom_errorbar(aes(ymin = mean_yIQR-se, ymax = mean_yIQR+se), position = position_dodge(0.9), width = 0.2) +
  theme_linedraw()

yiqr_lm <- lmer(yIQR ~ age + lang * direction + (1|name) + (1|story), data = iqr)
summary(yiqr_lm)
confint(yiqr_lm)
#ggcoef(yiqr_lm)
```

### Viewing Area
Description.

```{r}
area_mean <- iqr %>% 
  group_by(lang, direction, name) %>%
  summarise(area = mean(area, na.rm = T)) %>% # gets average looking percent for each baby
  group_by(lang, direction) %>%
  summarise(area_mean = mean(area), # gets group averages
            count = n(),
            sd = sd(area),
            se = sd/sqrt(count)) %>%
  select(-sd) %>%
  print()

# Plot
ggplot(iqr, aes(x = age, y = area, color = direction, fill = direction)) + 
  geom_jitter(alpha = 0.5) + 
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw() + 
  theme(panel.grid.major.x = element_blank()) +
  facet_grid(. ~ lang) +
  ggtitle("Viewing Area") +
  xlab("") +
  ylab("Area (px^2)")

ggplot(area_mean, aes(x = lang, y = area_mean, fill = direction)) +
  geom_bar(stat = "identity", position = position_dodge()) + 
  geom_errorbar(aes(ymin = area_mean-se, ymax = area_mean+se), position = position_dodge(0.9), width = 0.2) +
  theme_linedraw()

area_lm <- lmer(area ~ age + lang * direction + (1|name) + (1|story), data = iqr)
summary(area_lm)
confint(area_lm)
#ggcoef(area_lm)
```

## Plotting Viewing Area 

```{r}
medians <- iqr %>%
  group_by(name,lang,direction) %>%
  summarise(xIQR = mean(xIQR,na.rm=TRUE),
                   yIQR = mean(yIQR,na.rm=TRUE),
                   xmed = mean(xmed,na.rm=TRUE),
                   ymed = mean(ymed,na.rm=TRUE)) %>%
  group_by(lang,direction) %>% 
  summarise(xIQR = mean(xIQR,na.rm=TRUE),
                   yIQR = mean(yIQR,na.rm=TRUE),
                   x = mean(xmed,na.rm=TRUE),
                   y = mean(ymed,na.rm=TRUE)) %>%
  mutate(y = y*-1,
         xmin = x-(xIQR/2),
         xmax = x+(xIQR/2),
         ymin = y-(yIQR/2),
         ymax = y+(yIQR/2))
img <- png::readPNG("cindy.png")
g <- grid::rasterGrob(img, interpolate=TRUE, width=unit(1,"npc"), height=unit(1,"npc")) 
ggplot(medians, aes(fill=direction,color=direction)) +
  annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
  geom_rect(aes(xmin=xmin,ymin=ymin,xmax=xmax,ymax=ymax),alpha=.1) + 
  theme_linedraw() +
  scale_x_continuous(limits = c(0,1080), expand = c(0, 0)) +
  scale_y_continuous(limits = c(-720,0), expand = c(0, 0)) +
  facet_wrap("lang")
```

# XY Space Data - Multiple Plots

First let's prep the data. 
```{r}
multiples <- xydata %>%
  filter(!is.na(x)) %>%
  filter(!is.na(y)) %>%
  group_by(name, age, lang, story, direction, trial) %>%
  summarise(xIQR = IQR(x,na.rm=TRUE),
            yIQR = IQR(y,na.rm=TRUE),
            xmed = median(x, na.rm=TRUE),
            ymed = median(y, na.rm=TRUE),
            area = xIQR*yIQR,
            x_90 = quantile(x, .95, na.rm=TRUE) - quantile(x, .05, na.rm=TRUE),
            y_90 = quantile(y, .95, na.rm=TRUE) - quantile(y, .05, na.rm=TRUE),
            area_90 = (x_90) * (y_90),
            x_mean = mean(x, na.rm = TRUE),
            y_mean = mean(y, na.rm = TRUE),
            x_sd = sd(x, na.rm = TRUE),
            y_sd = sd(y, na.rm = TRUE),
            x_1sd = (x_mean+x_sd) - (x_mean-x_sd),
            y_1sd = (y_mean+y_sd) - (y_mean-y_sd),
            area_1sd = x_1sd * y_1sd,
            x_2sd = (x_mean+(x_sd*2)) - (x_mean-(x_sd*2)),
            y_2sd = (y_mean+(y_sd*2)) - (y_mean-(y_sd*2)),
            area_2sd = x_2sd * y_2sd) %>%
  group_by(name, lang, direction) %>%
  summarise_if(is.double, funs(mean), na.rm = T) %>%
  group_by(lang, direction) %>%
  summarise_if(is.double, funs(mean), na.rm = T)

img <- png::readPNG("cindy.png")
g <- grid::rasterGrob(img, interpolate=TRUE, width=unit(1,"npc"), height=unit(1,"npc")) 

```

## IQR (Middle 50%)
Let's see. 
```{r}
curr_data <- multiples %>% 
  ungroup() %>%
  select(lang, direction, xmed, ymed, xIQR, yIQR) %>%
  group_by(lang, direction) %>%
  summarise(xmin = xmed-(xIQR/2),
         xmax = xmed+(xIQR/2),
         ymin = -1*(ymed-(yIQR/2)),
         ymax = -1*(ymed+(yIQR/2)))

ggplot(curr_data, aes(fill=direction,color=direction)) +
  annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
  geom_rect(aes(xmin=xmin,ymin=ymin,xmax=xmax,ymax=ymax),alpha=.1) + 
  theme_linedraw() +
  scale_x_continuous(limits = c(0,1080), expand = c(0, 0)) +
  scale_y_continuous(limits = c(-720,0), expand = c(0, 0)) +
  facet_wrap("lang")
```

## Middle 90%
So I calculated the average median across, and the middle 90% of the data. 
```{r}
curr_data <- multiples %>% 
  ungroup() %>%
  select(lang, direction, xmed, ymed, x_90, y_90) %>%
  group_by(lang, direction) %>%
  summarise(xmin = xmed-(x_90/2),
         xmax = xmed+(x_90/2),
         ymin = -1*(ymed-(y_90/2)),
         ymax = -1*(ymed+(y_90/2)))

ggplot(curr_data, aes(fill=direction,color=direction)) +
  annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
  geom_rect(aes(xmin=xmin,ymin=ymin,xmax=xmax,ymax=ymax),alpha=.1) + 
  theme_linedraw() +
  scale_x_continuous(limits = c(0,1080), expand = c(0, 0)) +
  scale_y_continuous(limits = c(-720,0), expand = c(0, 0)) +
  facet_wrap("lang")

# ggplot(filter(curr_data, lang == "NSE"), aes(fill=direction,color=direction)) +
#   annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
#   geom_rect(aes(xmin=xmin,ymin=ymin,xmax=xmax,ymax=ymax),alpha=.2, size = 1) +
#   theme_linedraw() +
#   scale_x_continuous(limits = c(0,1080), expand = c(0, 0)) +
#   scale_y_continuous(limits = c(-720,0), expand = c(0, 0))
# 
# 
# ggplot(filter(curr_data, lang == "SE"), aes(fill=direction,color=direction)) +
#   annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
#   geom_rect(aes(xmin=xmin,ymin=ymin,xmax=xmax,ymax=ymax),alpha=.2, size = 1) +
#   theme_linedraw() +
#   scale_x_continuous(limits = c(0,1080), expand = c(0, 0)) +
#   scale_y_continuous(limits = c(-720,0), expand = c(0, 0))
```

## ±1 SD (Middle 68%)
So this is using the mean of the means, plus or minus one SD.  This is equivalent to middle 68%. 
```{r}
curr_data <- multiples %>% 
  ungroup() %>%
  select(lang, direction, x_mean, y_mean, x_1sd, y_1sd) %>%
  group_by(lang, direction) %>%
  summarise(xmin = x_mean-(x_1sd/2),
         xmax = x_mean+(x_1sd/2),
         ymin = -1*(y_mean-(y_1sd/2)),
         ymax = -1*(y_mean+(y_1sd/2)))

ggplot(curr_data, aes(fill=direction,color=direction)) +
  annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
  geom_rect(aes(xmin=xmin,ymin=ymin,xmax=xmax,ymax=ymax),alpha=.1) + 
  theme_linedraw() +
  scale_x_continuous(limits = c(0,1080), expand = c(0, 0)) +
  scale_y_continuous(limits = c(-720,0), expand = c(0, 0)) +
  facet_wrap("lang")
```

## ±2 SD (Middle 96%)
And this is using the mean of the means, plus or minus two SD.  This is equivalent to middle 96%. 
```{r}
curr_data <- multiples %>% 
  ungroup() %>%
  select(lang, direction, x_mean, y_mean, x_2sd, y_2sd) %>%
  group_by(lang, direction) %>%
  summarise(xmin = x_mean-(x_2sd/2),
         xmax = x_mean+(x_2sd/2),
         ymin = -1*(y_mean-(y_2sd/2)),
         ymax = -1*(y_mean+(y_2sd/2)))

ggplot(curr_data, aes(fill=direction,color=direction)) +
  annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
  geom_rect(aes(xmin=xmin,ymin=ymin,xmax=xmax,ymax=ymax),alpha=.1) + 
  theme_linedraw() +
  scale_x_continuous(limits = c(0,1080), expand = c(0, 0)) +
  scale_y_continuous(limits = c(-720,0), expand = c(0, 0)) +
  facet_wrap("lang")
```