---
title: "PuppiesXY (study2children)"
author: "Adam Stone, PhD" 
date: '`r format(Sys.Date(), "%m-%d-%Y")`'
output:
  html_notebook:
    code_folding: hide
    theme: spacelab
    highlight: tango
    toc: yes
    toc_depth: 2
    toc_float: yes
    df_print: paged
---

```{r eval=FALSE, include=FALSE}
# This is to get all kids' _processed_ puppiesxy.data into one single file. Should only run when needed. 
library(tidyverse)
library(feather)

csvpath = "../Child Data/_xypuppies/"
#csvpath = "~/Desktop/"
files <- dir(path = csvpath, pattern = "_xypuppies")
files <- paste(csvpath, files, sep="")
data <- files %>%
  map(read_csv) %>%
  reduce(rbind)
write_feather(data, "xypuppies.feather")
```

For now we're just working with babies. So that means we need to pull baby info from `cleanedbabyeyedata.feather`. Below is a table of how many rows of data each baby has. 

```{r message=FALSE}
# Libraries
library(tidyverse)
library(feather)
library(lme4)
library(lmerTest)

# Import data 
data <- read_feather("xypuppies.feather") %>%
  select(participant, condition, trial, x, y) %>%
  rename(name = participant)

# Pull baby names/info
babies <- read_feather("cleanedbabyeyedata.feather") %>%
  mutate(age = age*12) %>%
  select(participant, language, age) %>%
  rename(name = participant) %>%
  mutate(agegroup = case_when(
    age <= 8.99 ~ "younger",
    age >= 9.0 & age < 15 ~ "older"
  )) %>%
  filter(!is.na(agegroup)) %>%
  distinct()

# Filter that with xypuppies data
data <- left_join(babies, data, by = "name")
data %>% count(name)
```

And let's get means per trial per baby. 
```{r}
data_stats <- data %>%
  group_by(name, age, language, condition, trial) %>%
  summarise(x = mean(x, na.rm=TRUE),
            y = mean(y, na.rm=TRUE))
data_stats
```

Let's visualize. Remember not all the puppy pictures are the same size, though. 

```{r}
ggplot(data_stats, aes(x = x, y = -1*y, color = language)) + geom_point(alpha = 0.5) + facet_wrap("condition") + theme_linedraw() + xlab("mean x position") + ylab("mean y position")
```

And run a linear mixed model. First, x-axis - no differences of group (p = .52) or of age (p = .87) or interactions. Great!

```{r}
lmm_x <- lmer(data = data_stats, x ~ language * age + (1|condition) + (1|name))
summary(lmm_x)
```

Next, y-axis - no NSE/SE differences (p = 0.82) but there is an effect of age (p = 0.03)!! Interesting. 

```{r}
lmm_y <- lmer(data = data_stats, y ~ language * age + (1|condition) + (1|name))
summary(lmm_y)
```

Let's explore the effect of age on the y-axis some more...this tells us there IS an effect but it's very subtle. And the LMM output above tells us that it's about 4 pixels for every month. So a 12-month-old looks about 29 pixels lower compared to a 6-month-old. That is nothing, it's not half of an AOI. It's a significant effect, but it's a tiny thing and likely nothing to worry about. I think!!

```{r}
ggplot(data_stats, aes(x = age, y = -1*y)) + geom_point(alpha = 0.5, aes(color = language)) + geom_smooth(method = "lm") + facet_wrap("condition") + theme_linedraw() + ylab("mean y position") +
  xlab("age (months)")
```

# Shifting 4 babies

How do results change if I shift 4 babies? 

```{r}
data2 <- data_stats %>%
  mutate(y = case_when(
    name == "aubrey CODA 11m" ~ y-15,
    name == "LA11BA11_5M_24D" ~ y-50,
    name == "Parker 6 m SIGNING" ~ y-61,
    name == "Trinity 8m" ~ y-40,
    TRUE ~ y
  ))

ggplot(data2, aes(x = x, y = -1*y, color = language)) + geom_point(alpha = 0.5) + facet_wrap("condition") + theme_linedraw() + xlab("mean x position") + ylab("mean y position")
```

Now re-run the linear model for y-axis. The age effect is more significant (p = 0.005) and the magnitude is now 5.7 pixels per month. 12-month-olds look 34 pixels lower than 6-month-olds. 

```{r}
lmm_y <- lmer(data = data2, y ~ language * age + (1|condition) + (1|name))
summary(lmm_y)
```

And the visualization.

```{r}
ggplot(data2, aes(x = age, y = -1*y)) + geom_point(alpha = 0.5, aes(color = language)) + geom_smooth(method = "lm") + facet_wrap("condition") + theme_linedraw() + ylab("mean y position") +
  xlab("age (months)")
```

