---
title: "TwoPuppies (study2children)"
author: "Adam Stone, PhD" 
date: '`r format(Sys.Date(), "%m-%d-%Y")`'
output:
  html_notebook:
    code_folding: hide
    theme: spacelab
    highlight: tango
    toc: yes
    toc_depth: 2
    toc_float: yes
    df_print: paged
---

```{r eval=FALSE, include=FALSE}
# This is to get all kids' _processed_ TwoPuppies data into one single file. Should only run when needed. 
library(tidyverse)
library(feather)

csvpath = "../Child Data/_twopuppies/"
#csvpath = "~/Desktop/"
files <- dir(path = csvpath, pattern = "_TwoPuppiesData")
files <- paste(csvpath, files, sep="")
data <- files %>%
  map(read_csv) %>%
  reduce(rbind)
write_feather(data, "twopuppies.feather")
```

Let's get all the puppy data and see histograms. 

```{r message=FALSE}
# Libraries
library(tidyverse)
library(feather)
#library(stringr)
#library(cowplot)

# Import data 
data <- read_feather("twopuppies.feather") %>%
  mutate(puppy = case_when(
    mark == 1 ~ "chihuahua",
    mark == 2 ~ "frisby"
  ))

# Get ages
# ages <- read_csv("childrenages.csv")
# data <- data %>% left_join(ages, by = "participant")
# data %>% select(participant,language,age) %>% distinct() # print data table

# Histogram of ages
data <- data %>% rename(x = xpos, y = ypos) %>%
  gather(axis, pos, x:y)

ggplot(data, aes(x = pos, fill = axis)) + geom_histogram(binwidth = 10) + ggtitle("X/Y Histogram for Puppies") + facet_grid(puppy ~ axis)
```

And let's get mean and medians
```{r}
data_stats <- data %>%
  group_by(puppy, axis) %>%
  summarise(mean = mean(pos, na.rm=TRUE),
         median = median(pos, na.rm=TRUE))
data_stats
globalmedian = data_stats$median
```

# Aubrey
```{r message=FALSE}
aubrey <- read_csv("../Child Data/_twopuppies/Aubrey_Rec 02_TwoPuppiesData.csv") %>%
  mutate(puppy = case_when(
    mark == 1 ~ "chihuahua",
    mark == 2 ~ "frisby"
  )) %>%
  rename(x = xpos, y = ypos) %>%
  gather(axis, pos, x:y)

ggplot(aubrey, aes(x = pos, fill = axis)) + geom_histogram(binwidth = 10) + ggtitle("X/Y Histogram for Puppies") + facet_grid(puppy ~ axis)

aubrey_stats <- aubrey %>%
  group_by(puppy, axis) %>%
  summarise(mean = mean(pos, na.rm=TRUE),
         median = median(pos, na.rm=TRUE)) %>%
  ungroup() %>%
  mutate(offset = median - globalmedian)
aubrey_stats
```

Aubrey's offsets are approximately: 
```{r}
aubrey_stats %>% group_by(axis) %>% summarise(offset = mean(offset))
```

Aubrey's data needs to be shifted RIGHT by 88 and UP by 15.

# Owen
Owen's data is misaligned. See below: 
```{r message=FALSE}
owen <- read_csv("../Child Data/_twopuppies/Owen twin 4y2m POOR CALIB_TwoPuppiesData.csv") %>%
  mutate(puppy = case_when(
    mark == 1 ~ "chihuahua",
    mark == 2 ~ "frisby"
  )) %>%
  rename(x = xpos, y = ypos) %>%
  gather(axis, pos, x:y)

ggplot(owen, aes(x = pos, fill = axis)) + geom_histogram(binwidth = 10) + ggtitle("X/Y Histogram for Puppies") + facet_grid(puppy ~ axis)

owen_stats <- owen %>%
  group_by(puppy, axis) %>%
  summarise(mean = mean(pos, na.rm=TRUE),
         median = median(pos, na.rm=TRUE)) %>%
  ungroup() %>%
  mutate(offset = median - globalmedian)
owen_stats
```

Owen's offsets are approximately: 
```{r}
owen_stats %>% group_by(axis) %>% summarise(offset = mean(offset))
```

Owen's data needs to be shifted RIGHT by 53 and DOWN by 73. 

# Lyla
I wanted to check Lyla's data. Becaues when I was checking for AOI outliers, I noticed Lyla had a lot of high AOI %'s on the chest. 
```{r message=FALSE}
lyla <- read_csv("../Child Data/_twopuppies/Rec 09 Lyla GREAT_TwoPuppiesData.csv") %>%
  mutate(puppy = case_when(
    mark == 1 ~ "chihuahua",
    mark == 2 ~ "frisby"
  )) %>%
  rename(x = xpos, y = ypos) %>%
  gather(axis, pos, x:y)

ggplot(lyla, aes(x = pos, fill = axis)) + geom_histogram(binwidth = 10) + ggtitle("X/Y Histogram for Puppies") + facet_grid(puppy ~ axis)

lyla_stats <- lyla %>%
  group_by(puppy, axis) %>%
  summarise(mean = mean(pos, na.rm=TRUE),
         median = median(pos, na.rm=TRUE)) %>%
  ungroup() %>%
  mutate(offset = median - globalmedian)
lyla_stats
```

I don't like her data for Chihuahua (seems scattered) so let's only use Frisby to calculate offset 

Lyla's offsets are approximately: 
```{r}
lyla_stats %>% filter(puppy=='frisby') %>% select(axis, offset)
```

Lyla's data needs to be shifted LEFT by 7 and UP by 68. That sounds just about right! I would just move it up vertically by 68, and not worry about horizontal offsets. 

# Mason
I wanted to check Mason's data because I noticed he had a lot of high MidFaceCenter AOI percentages.
```{r message=FALSE}
mason <- read_csv("../Child Data/_twopuppies/Mason_CODA_6y_GOOD_TwoPuppiesData.csv") %>%
  mutate(puppy = case_when(
    mark == 1 ~ "chihuahua",
    mark == 2 ~ "frisby"
  )) %>%
  rename(x = xpos, y = ypos) %>%
  gather(axis, pos, x:y)

ggplot(mason, aes(x = pos, fill = axis)) + geom_histogram(binwidth = 10) + ggtitle("X/Y Histogram for Puppies") + facet_grid(puppy ~ axis)

mason_stats <- mason %>%
  group_by(puppy, axis) %>%
  summarise(mean = mean(pos, na.rm=TRUE),
         median = median(pos, na.rm=TRUE)) %>%
  ungroup() %>%
  mutate(offset = median - globalmedian)
mason_stats
```

Mason's offsets are approximately: 
```{r}
mason_stats %>% group_by(axis) %>% summarise(offset = mean(offset))
```

Mason's data needs to be shifted LEFT by 34 and UP by 10. Mabye that's peanuts and we can leave it alone. At the most, the x-offset seems consistent so maybe we should correct horizontal offset? While the y-offset appears to be zero and we can leave it alone. 


# Ainsley
I wanted to check Ainsley's data as an example of a GOOD kid...what kind of offsets would we see? 
```{r message=FALSE}
ainsley <- read_csv("../Child Data/_twopuppies/Ainsely 5y1m GREAT_TwoPuppiesData.csv") %>%
  mutate(puppy = case_when(
    mark == 1 ~ "chihuahua",
    mark == 2 ~ "frisby"
  )) %>%
  rename(x = xpos, y = ypos) %>%
  gather(axis, pos, x:y)

ggplot(ainsley, aes(x = pos, fill = axis)) + geom_histogram(binwidth = 10) + ggtitle("X/Y Histogram for Puppies") + facet_grid(puppy ~ axis)

ainsley_stats <- ainsley %>%
  group_by(puppy, axis) %>%
  summarise(mean = mean(pos, na.rm=TRUE),
         median = median(pos, na.rm=TRUE)) %>%
  ungroup() %>%
  mutate(offset = median - globalmedian)
ainsley_stats
```

Ainsley's offsets are approximately: 
```{r}
ainsley_stats %>% group_by(axis) %>% summarise(offset = mean(offset))
```

Ainsley's data needs to be shifted RIGHT by 13 and UP by 15. Which is nothing, so yes, it's well-calibrated. 

# CR03TA11
Checking CR03 - some high belly looking. 
```{r message=FALSE}
cr03 <- read_csv("../Child Data/_twopuppies/CR03TA11_13m no calib obtained_TwoPuppiesData.csv") %>%
  mutate(puppy = case_when(
    mark == 1 ~ "chihuahua",
    mark == 2 ~ "frisby"
  )) %>%
  rename(x = xpos, y = ypos) %>%
  gather(axis, pos, x:y)

ggplot(cr03, aes(x = pos, fill = axis)) + geom_histogram(binwidth = 10) + ggtitle("X/Y Histogram for Puppies") + facet_grid(puppy ~ axis)

cr03_stats <- cr03 %>%
  group_by(puppy, axis) %>%
  summarise(mean = mean(pos, na.rm=TRUE),
         median = median(pos, na.rm=TRUE)) %>%
  ungroup() %>%
  mutate(offset = median - globalmedian)
cr03_stats
```

CR03's offsets are approximately: 
```{r}
cr03_stats %>% group_by(axis) %>% summarise(offset = mean(offset))
```

Maybe a slight x axis offset to the right. But probably nothing to worry about. 

# Desmond
Checking Desmond - some high LeftChestBottom looking 
```{r message=FALSE}
desmond <- read_csv("../Child Data/_twopuppies/Desmond GOOD_TwoPuppiesData.csv") %>%
  mutate(puppy = case_when(
    mark == 1 ~ "chihuahua",
    mark == 2 ~ "frisby"
  )) %>%
  rename(x = xpos, y = ypos) %>%
  gather(axis, pos, x:y)

ggplot(desmond, aes(x = pos, fill = axis)) + geom_histogram(binwidth = 10) + ggtitle("X/Y Histogram for Puppies") + facet_grid(puppy ~ axis)

desmond_stats <- desmond %>%
  group_by(puppy, axis) %>%
  summarise(mean = mean(pos, na.rm=TRUE),
         median = median(pos, na.rm=TRUE)) %>%
  ungroup() %>%
  mutate(offset = median - globalmedian)
desmond_stats
```

Desmond's offsets are approximately: 
```{r}
desmond_stats %>% group_by(axis) %>% summarise(offset = mean(offset))
```

Nothing to worry about. 

# LA11BA11
Checking LA11BA11 - some high MidChestBottom looking 
```{r message=FALSE}
la11 <- read_csv("../Child Data/_twopuppies/LA11BA11_5M_24D_GOOD_TwoPuppiesData.csv") %>%
  mutate(puppy = case_when(
    mark == 1 ~ "chihuahua",
    mark == 2 ~ "frisby"
  )) %>%
  rename(x = xpos, y = ypos) %>%
  gather(axis, pos, x:y)

ggplot(la11, aes(x = pos, fill = axis)) + geom_histogram(binwidth = 10) + ggtitle("X/Y Histogram for Puppies") + facet_grid(puppy ~ axis)

la11_stats <- la11 %>%
  group_by(puppy, axis) %>%
  summarise(mean = mean(pos, na.rm=TRUE),
         median = median(pos, na.rm=TRUE)) %>%
  ungroup() %>%
  mutate(offset = median - globalmedian)
la11_stats
```

LA11's offsets are approximately: 
```{r}
la11_stats %>% group_by(axis) %>% summarise(offset = mean(offset))
```

Maybe y-axis should be looked at.


# MA01WA22
Checking MA01WA22 - several high MidFaceCenter and MidFaceTop looking 
```{r message=FALSE}
ma01 <- read_csv("../Child Data/_twopuppies/ma01wa22 10m GOOD_TwoPuppiesData.csv") %>%
  mutate(puppy = case_when(
    mark == 1 ~ "chihuahua",
    mark == 2 ~ "frisby"
  )) %>%
  rename(x = xpos, y = ypos) %>%
  gather(axis, pos, x:y)

ggplot(ma01, aes(x = pos, fill = axis)) + geom_histogram(binwidth = 10) + ggtitle("X/Y Histogram for Puppies") + facet_grid(puppy ~ axis)

ma01_stats <- ma01 %>%
  group_by(puppy, axis) %>%
  summarise(mean = mean(pos, na.rm=TRUE),
         median = median(pos, na.rm=TRUE)) %>%
  ungroup() %>%
  mutate(offset = median - globalmedian) %>%
  print()
```

MA01's offsets are approximately: 
```{r}
ma01_stats %>% group_by(axis) %>% summarise(offset = mean(offset))
```
Yeah look at the y-axis. 

# NI12GO05
Lots of high midchestcenter and midchestbottom
```{r message=FALSE}
ni12 <- read_csv("../Child Data/_twopuppies/NI12GO05_5M_4D_GOOD_TwoPuppiesData.csv") %>%
  mutate(puppy = case_when(
    mark == 1 ~ "chihuahua",
    mark == 2 ~ "frisby"
  )) %>%
  rename(x = xpos, y = ypos) %>%
  gather(axis, pos, x:y)

ggplot(ni12, aes(x = pos, fill = axis)) + geom_histogram(binwidth = 10) + ggtitle("X/Y Histogram for Puppies") + facet_grid(puppy ~ axis)

ni12_stats <- ni12 %>%
  group_by(puppy, axis) %>%
  summarise(mean = mean(pos, na.rm=TRUE),
         median = median(pos, na.rm=TRUE)) %>%
  ungroup() %>%
  mutate(offset = median - globalmedian) %>%
  print()
```

NI12's offsets are approximately: 
```{r}
ni12_stats %>% group_by(axis) %>% summarise(offset = mean(offset))
```
Should at least fix the y-axis.

# Brooke
Lots of high midchestcenter and midchestbottom
```{r message=FALSE}
brooke <- read_csv("../Child Data/_twopuppies/Rec 01 BAD CALIBRATION_TwoPuppiesData.csv") %>%
  mutate(puppy = case_when(
    mark == 1 ~ "chihuahua",
    mark == 2 ~ "frisby"
  )) %>%
  rename(x = xpos, y = ypos) %>%
  gather(axis, pos, x:y)

ggplot(brooke, aes(x = pos, fill = axis)) + geom_histogram(binwidth = 10) + ggtitle("X/Y Histogram for Puppies") + facet_grid(puppy ~ axis)

brooke_stats <- brooke %>%
  group_by(puppy, axis) %>%
  summarise(mean = mean(pos, na.rm=TRUE),
         median = median(pos, na.rm=TRUE)) %>%
  ungroup() %>%
  mutate(offset = median - globalmedian) %>%
  print()
```

Brooke's offsets are approximately: 
```{r}
brooke_stats %>% group_by(axis) %>% summarise(offset = mean(offset))
```

